### 2022-08-18 article.tex
init commit

\documentclass[anonymous,sigplan,review,11pt,nonacm,natbib=false]{acmart}
\settopmatter{printfolios=false,printccs=false,printacmref=false}
\usepackage[maxnames=1,minnames=1,maxbibnames=100,natbib=true,citestyle=authoryear,bibstyle=authoryear,doi=false,url=false,isbn=false,isbn=false]{biblatex}
\addbibresource{main.bib}

\usepackage[russian]{babel}

\usepackage{debate}
\usepackage{ffcode}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{MnSymbol}
\usepackage[capitalize]{cleveref}
\usepackage{paralist}
\usepackage{cancel}
\usepackage{to-be-determined}
\usepackage{tikz}

\acmBooktitle{untitled}
\title{Strings methods analysis}
\author{Yegor Bugayenko}
\email{yegor256@gmail.com}
\affiliation{Huawei\city{Moscow}\country{Russia}}
\ccsdesc[100]{Object-Oriented Programming}
\keywords{Object-Oriented  Programming}

\begin{document}
\raggedbottom

\begin{abstract}
\end{abstract}

\maketitle

\section{Introduction}\label{sec:intro}

A string is an ordered set of characters. The standard library of string methods varies from language to language. Then in the case of creating a new language, you need to build your own library based on some criteria. However, the number of different functionality methods for strings that can be invented is at least countable (to put it simply - infinite). Then what to base on to identify the necessary set of methods for an object-oriented language? \hl{<- RQ}

This article aims to make a multivariate analysis of different parameters of string methods.

We should keep in mind that the number of string methods in different programming languages is very large, and this number can grow, as we said before, without limitations. For this reason, this article does not consider all existing methods, but only those that meet some criteria.

An important factor for any method will be the frequency of its use in the code. In this article we will describe the algorithm, according to which we will evaluate this parameter. We will also investigate the accuracy of these estimates, since there is no absolutely accurate method for estimating this parameter in a reasonable amount of time.

Another important parameter that is investigated in this article is the number of uses of one method, inside (for realization) the others. This criterion allows us to identify important dependencies of some methods on others.

An algorithm to obtain the minimum set of required string methods will be created. This algorithm will be analyzed for susceptibility to bias, since it depends on the initial input data.

Also an important parameter for methods (in this case string methods) is their running time, so this article also considers this parameter. An interesting question is: will mutable or immutable structures be considered? Since this is a complex analysis, both are considered. And also the regularities in the interrelation of mutable and nonmutable methods asymptotics are revealed.

The article then discusses the results obtained and evaluates them. The accuracy of the obtained data is also evaluated. And a conclusion is made: which set of methods we took for our language.

\section{Related work}

Among the other publications on this topic that exist at the time of this writing, all are of an applied nature. For this reason, they are not discussed in this article. In our article, we provide data that can be used in a free form, including for creating our own string libraries.

\section{Considered methods}

In order to investigate methods, we have to make a list of methods to be investigated. For this purpose, programming languages such as Java, Python, C++, Ruby were chosen. They were chosen on the basis that they are quite popular, and they implement different paradigms (e.g. strict and non-strict typing in C++ and Python respectively).

A table with the list of different methods from standard string libraries for these languages has been compiled. For the analysis will be selected methods, which are presented at least in two programming languages (out of four presented). Since for the methods presented only in one language, we can conclude that they are used in too special or rare cases.

To avoid self-repeats, a summary list of the methods to be analyzed is presented in Section 8.

\section{Popularity of methods}

\subsection{Definition}

Since popularity is a measurable parameter, let's calculate the number of uses of each string method (see below). Then we denote popularity as a percentage of the number of uses of a certain string method relative to the total number of uses of all string methods. This approach makes it possible to estimate the frequency of string methods usage exactly in the context of correlation with other string methods.

\subsection{Search algorithm}

The GitHub and Sourcegraph platforms were chosen to calculate the number of uses of the methods. This platform provides the ability to search for any words or phrases in all GitHub projects, as well as if necessary to specify other parameters.

However, you should take into account that asking for the number of times a certain word occurs in the code in certain cases will not give a correct result, there are a number of reasons for that.

\subsubsection{The word is a comment} \hl{}

For some words, it is more common for them to appear in files as names/comments/inside strings rather than as called functions. Since the article deals with the use of string methods for object-oriented languages, and they use dot notation, it will be more efficient to make queries like .<method name>, instead of <method name>.

\subsubsection{It's a another class method} \hl{}

In this kind of analysis, for some methods there is a problem that it is not clear which class of objects has which method. For example, the contains method is present in string as well as in most collections.

Of course, it makes sense to examine the context in which the methods were used. However, this task is difficult because of the large amount of data to be analyzed.

It is worth noting that methods which have had this problem are popular (note here that we mean methods for all classes, not specifically string methods), this we have obtained by making queries about the number of times they occur for code bases. For this reason, this data will not be counted in this article, but a method for solving this problem is given in the Discussion section.

\section{Mutual usages}

For any method (in our case string methods) you can consider such a parameter as its use by other methods. It is important because it is impossible to exclude a method from the library in case many other methods of the library use it.

This parameter will be an integer numeric value that will be equal to the number of methods that can use it in their implementation (that is, it should not just be present in the implementation, but be necessary there) without affecting the asymptotics.

\section{Asymptotics}

\subsection{Mutable}

In order to define the asymptotics of the different string methods, let us define what a string is. Since we are considering mutable strings, we consider a string to be an array of characters with which we can use write and read operations. This way we can avoid copying for every mutable operation.

To understand more about the advantages of this approach: we can change any character of a string in a constant amount of time, because we won't have to copy anything. However, in order to take a substring of the string, we will have to explicitly create a new string - this is a disadvantage.

\subsection{Immutable}

Immutable strings impose a number of constraints on the operation. We define immutable strings as an array of characters where we are allowed to read characters in a constant time, and each mutable operation creates a new copy. We are also allowed to store a constant number of other variables, such as various flags.

However, no additional restrictions are imposed, for example, in mutable operations we can refer to past versions.

To better understand what advantages this approach gives: if we need to take a substring of a string, we can do it in a constant time, because due to immutability we can simply refer to characters inside the old string. However, for example, the operation to replace the last character of the string will take linear time from the length of the string.

\section{Finding the minimum set}

\subsection{Necessity}

Even if there are various criteria for methods, it is still necessary to determine how to get a library based on them. Therefore, we propose an algorithm that can be used for various (including not yet existing) object-oriented programming languages.

\subsection{Parameter setting}

It is necessary to set a criterion on the basis of which a decision will be made whether to add a method to the current set of methods.

As an example, consider the following criterion: a method cannot be implemented through three or less methods existing in the set, so that its asymptotics is not degraded.

\subsection{Algorithm}

Now specifically about the algorithm on the basis of which the final set of methods will be obtained.

\begin{enumerate}
    \item Set is initially empty.
    \item Functions are considered in priority order, by default the most popular methods come first. If the method meets criterion 7.2, it is added to the set.
    \item The second step is repeated until there are no unselected methods left.
    \item In reverse order of priority the methods in the set are considered and those that don't meet criterion 7.2 are removed.
\end{enumerate}

\section{Results}

Below is a table with the results - metrics.

\begin{table*}[]
    \centering
    \begin{tabular}{|c||c|c|c|c|}
        \hline
         & Popularity & Mutual usages & Mutable O(?) & Immutable O(?) \\ \hline \hline
        capitalize &  &  & 1 & 1 \\ \hline

        char-at &  &  & 1 & 1 \\ \hline

        compare &  &  & n & n \\ \hline

        compare-ignore-case &  &  &  & \\ \hline

        concatenate &  &  & n & n \\ \hline

        containts &  &  & n & n \\ \hline

        count &  &  &  & \\ \hline

        ends-with &  &  & n & n \\ \hline

        equals &  &  & n & n \\ \hline

        find-first &  &  & n & n \\ \hline

        find-last &  &  & n & n \\ \hline

        format &  &  & n & n \\ \hline

        hash &  &  & n & n \\ \hline

        insert &  &  & n & n \\ \hline

        is-alphabetic &  &  & n & n \\ \hline

        is-empty &  &  & 1 & 1 \\ \hline

        is-hexadecimal &  &  & n & n \\ \hline

        is-int &  &  & n & n \\ \hline

        is-lowercase &  &  & n & n \\ \hline

        is-uppercase &  &  & n & n \\ \hline

        is-whitespace &  &  & n & n \\ \hline

        join &  &  & n & n \\ \hline

        length &  &  & 1 & 1 \\ \hline

        matches-regexp &  &  & n & n \\ \hline

        partition &  &  & n & n \\ \hline

        repeat &  &  & n & n \\ \hline

        replace-all &  &  & n & n \\ \hline

        replace-first  &  &  &  & \\ \hline

        split &  &  & n & n \\ \hline

        starts-with &  &  & n & n \\ \hline

        strip &  &  & n & n \\ \hline

        substring &  &  & n & 1 \\ \hline

        swap-case &  &  & n & n \\ \hline

        to-float &  &  & n & n \\ \hline

        to-int &  &  & n & n \\ \hline

        to-lowercase &  &  & n & n \\ \hline

        to-uppercase &  &  & n & n \\ \hline

        trim-left &  &  & n & n \\ \hline

        trim-right &  &  & n & n \\ \hline

        reverse &  &  & n & 1 \\ \hline

        remove &  &  &  & \\ \hline

        uncapitalize &  &  &  & \\ \hline

        as-bytes &  &  &  & \\ \hline

        chop &  &  &  & \\ \hline

        clear &  &  &  & \\ \hline

    \end{tabular}
    \caption{String methods criteria}
    \label{tab:my_label}
\end{table*}

Based on these data, we have compiled our optimal library for string methods; the included methods are listed below.

\hl{todo}

\section{Discussion and analysis}

\subsection{Mutual usages presenting}

When we counted the Mutual usages parameter we used a numerical value. However, it is worth considering that a representation in the form of an oriented dependency graph would give more applied information. Because based on this graph, it would be less biased to construct a minimal set of string methods.

However, it is not possible to represent the graph in this paper because the number of its edges would be too large (of the order of the square of the number of methods). And such representation would lose any comprehensible visualization.

\subsection{Problems with method intersection}

Earlier we mentioned the problem with popularity calculation for methods that have the same name, but are called on objects of different classes.

To solve this problem we propose to use probabilistic approach. Suppose we need to know how many times a method with name Y has been used on string. Randomly gather a sample of files where this word Y occurs. Analyze what percentage of them uses word Y as a string method. Also find out the total number of times word Y was used in the code. Multiplying the total number by the probability we will get the answer. 
In fact, we will apply the extrapolation method.

Note that this method does not show absolute accuracy; however, if the files to be analyzed are selected at random, the error decreases very much.

In order to estimate the error it is necessary to take several similar samples and compare how different the results are.

\subsection{Unexpected advantage of immutability}

\hl{todo}

\section{Conclusion}\label{sec:conclusion}

\hl{todo}

\section{Used materials}

\hl{todo}

\printbibliography

\end{document}

### 2022-08-18 article.tex
examples of mutability/immutability removed

@@
 
-To understand more about the advantages of this approach: we can change any character of a string in a constant amount of time, because we won't have to copy anything.
-However, in order to take a substring of the string, we will have to explicitly create a new string - this is a disadvantage.
-
     \subsection{Immutable}
@@
 We are also allowed to store a constant number of other variables, such as various flags.
-
-However, no additional restrictions are imposed, for example, in mutable operations we can refer to past versions.
-
-To better understand what advantages this approach gives: if we need to take a substring of a string, we can do it in a constant time, because due to immutability we can simply refer to characters inside the old string.
-However, for example, the operation to replace the last character of the string will take linear time from the length of the string.
 

### 2022-08-19 article.tex
extrapolation method simplified

@@
 
-    To solve this problem we propose to use probabilistic approach.
-Suppose we need to know how many times a method with name Y has been used on string.
-Randomly gather a sample of files where this word Y occurs.
-Analyze what percentage of them uses word Y as a string method.
-Also find out the total number of times word Y was used in the code.
-Multiplying the total number by the probability we will get the answer.
-    In fact, we will apply the extrapolation method.
+    To solve this problem we can apply the extrapolation method here.
 

### 2022-08-19 article.tex
parameter setting example removed
introduction simplified

@@
 
-    An important factor for any method will be the frequency of its use in the code.
-In this article we will describe the algorithm, according to which we will evaluate this parameter.
-We will also investigate the accuracy of these estimates, since there is no absolutely accurate method for estimating this parameter in a reasonable amount of time.
+    An important factor for any method will be the frequency of its use in the code. In this article we will describe the algorithm, according to which we will evaluate this parameter.
 
@@
     Also an important parameter for methods (in this case string methods) is their running time, so this article also considers this parameter.
-An interesting question is: will mutable or immutable structures be considered?
-Since this is a complex analysis, both are considered.
-And also the regularities in the interrelation of mutable and nonmutable methods asymptotics are revealed.
+Since this is a complex analysis, the asymptotics of mutable and immutable string functions will be analyzed, as well as the asymptotics under full language immutability.
 
@@
     It is necessary to set a criterion on the basis of which a decision will be made whether to add a method to the current set of methods.
-
-    As an example, consider the following criterion: a method cannot be implemented through three or less methods existing in the set, so that its asymptotics is not degraded.
 

### 2022-08-19 article.tex
method changed to function

@@
 \acmBooktitle{untitled}
-\title{Strings methods analysis}
+\title{Strings functions analysis}
 \author{Yegor Bugayenko}
@@
     A string is an ordered set of characters.
-The standard library of string methods varies from language to language.
+The standard library of string functions varies from language to language.
 Then in the case of creating a new language, you need to build your own library based on some criteria.
-However, the number of different functionality methods for strings that can be invented is at least countable (to put it simply - infinite).
-Then what to base on to identify the necessary set of methods for an object-oriented language?
+However, the number of different functionality functions for strings that can be invented is at least countable (to put it simply - infinite).
+Then what to base on to identify the necessary set of functions for an object-oriented language?
 \hl{<- RQ}
 
-    This article aims to make a multivariate analysis of different parameters of string methods.
+    This article aims to make a multivariate analysis of different parameters of string functions.
 
-    We should keep in mind that the number of string methods in different programming languages is very large, and this number can grow, as we said before, without limitations.
-For this reason, this article does not consider all existing methods, but only those that meet some criteria.
+    We should keep in mind that the number of string functions in different programming languages is very large, and this number can grow, as we said before, without limitations.
+For this reason, this article does not consider all existing functions, but only those that meet some criteria.
 
-    An important factor for any method will be the frequency of its use in the code. In this article we will describe the algorithm, according to which we will evaluate this parameter.
+    An important factor for any function will be the frequency of its use in the code. In this article we will describe the algorithm, according to which we will evaluate this parameter.
 
-    Another important parameter that is investigated in this article is the number of uses of one method, inside (for realization) the others.
-This criterion allows us to identify important dependencies of some methods on others.
+    Another important parameter that is investigated in this article is the number of uses of one function, inside (for realization) the others.
+This criterion allows us to identify important dependencies of some functions on others.
 
-    An algorithm to obtain the minimum set of required string methods will be created. This algorithm will be analyzed for susceptibility to bias, since it depends on the initial input data.
+    An algorithm to obtain the minimum set of required string functions will be created. This algorithm will be analyzed for susceptibility to bias, since it depends on the initial input data.
 
-    Also an important parameter for methods (in this case string methods) is their running time, so this article also considers this parameter.
+    Also an important parameter for functions (in this case string functions) is their running time, so this article also considers this parameter.
 Since this is a complex analysis, the asymptotics of mutable and immutable string functions will be analyzed, as well as the asymptotics under full language immutability.
 
-    The article then discusses the results obtained and evaluates them. The accuracy of the obtained data is also evaluated. And a conclusion is made: which set of methods we took for our language.
+    The article then discusses the results obtained and evaluates them. The accuracy of the obtained data is also evaluated. And a conclusion is made: which set of functions we took for our language.
 
@@
 
-    \section{Considered methods}
+    \section{Considered functions}
 
-    In order to investigate methods, we have to make a list of methods to be investigated.
+    In order to investigate functions, we have to make a list of functions to be investigated.
 For this purpose, programming languages such as Java, Python, C++, Ruby were chosen.
@@
 
-    A table with the list of different methods from standard string libraries for these languages has been compiled.
-For the analysis will be selected methods, which are presented at least in two programming languages (out of four presented).
-Since for the methods presented only in one language, we can conclude that they are used in too special or rare cases.
+    A table with the list of different functions from standard string libraries for these languages has been compiled.
+For the analysis will be selected functions, which are presented at least in two programming languages (out of four presented).
+Since for the functions presented only in one language, we can conclude that they are used in too special or rare cases.
 
-    To avoid self-repeats, a summary list of the methods to be analyzed is presented in Section 8.
+    To avoid self-repeats, a summary list of the functions to be analyzed is presented in Section 8.
 
-    \section{Popularity of methods}
+    \section{Popularity of functions}
 
@@
 
-    Since popularity is a measurable parameter, let's calculate the number of uses of each string method (see below).
-Then we denote popularity as a percentage of the number of uses of a certain string method relative to the total number of uses of all string methods.
-This approach makes it possible to estimate the frequency of string methods usage exactly in the context of correlation with other string methods.
+    Since popularity is a measurable parameter, let's calculate the number of uses of each string function (see below).
+Then we denote popularity as a percentage of the number of uses of a certain string function relative to the total number of uses of all string functions.
+This approach makes it possible to estimate the frequency of string functions usage exactly in the context of correlation with other string functions.
 
@@
 
-    The GitHub and Sourcegraph platforms were chosen to calculate the number of uses of the methods.
+    The GitHub and Sourcegraph platforms were chosen to calculate the number of uses of the functions.
 This platform provides the ability to search for any words or phrases in all GitHub projects, as well as if necessary to specify other parameters.
@@
     For some words, it is more common for them to appear in files as names/comments/inside strings rather than as called functions.
-Since the article deals with the use of string methods for object-oriented languages, and they use dot notation, it will be more efficient to make queries like .<method name>, instead of <method name>.
+Since the article deals with the use of string functions for object-oriented languages, and they use dot notation, it will be more efficient to make queries like .<function name>, instead of <function name>.
 
-    \subsubsection{It's a another class method} \hl{}
+    \subsubsection{It's a another class function} \hl{}
 
-    In this kind of analysis, for some methods there is a problem that it is not clear which class of objects has which method.
-For example, the contains method is present in string as well as in most collections.
+    In this kind of analysis, for some functions there is a problem that it is not clear which class of objects has which function.
+For example, the contains function is present in string as well as in most collections.
 
-    Of course, it makes sense to examine the context in which the methods were used. However, this task is difficult because of the large amount of data to be analyzed.
+    Of course, it makes sense to examine the context in which the functions were used. However, this task is difficult because of the large amount of data to be analyzed.
 
-    It is worth noting that methods which have had this problem are popular (note here that we mean methods for all classes, not specifically string methods), this we have obtained by making queries about the number of times they occur for code bases.
-For this reason, this data will not be counted in this article, but a method for solving this problem is given in the Discussion section.
+    It is worth noting that functions which have had this problem are popular (note here that we mean functions for all classes, not specifically string functions), this we have obtained by making queries about the number of times they occur for code bases.
+For this reason, this data will not be counted in this article, but a function for solving this problem is given in the Discussion section.
 
@@
 
-    For any method (in our case string methods) you can consider such a parameter as its use by other methods.
-It is important because it is impossible to exclude a method from the library in case many other methods of the library use it.
+    For any function (in our case string functions) you can consider such a parameter as its use by other functions.
+It is important because it is impossible to exclude a function from the library in case many other functions of the library use it.
 
-    This parameter will be an integer numeric value that will be equal to the number of methods that can use it in their implementation (that is, it should not just be present in the implementation, but be necessary there) without affecting the asymptotics.
+    This parameter will be an integer numeric value that will be equal to the number of functions that can use it in their implementation (that is, it should not just be present in the implementation, but be necessary there) without affecting the asymptotics.
 
@@
 
-    In order to define the asymptotics of the different string methods, let us define what a string is.
+    In order to define the asymptotics of the different string functions, let us define what a string is.
 Since we are considering mutable strings, we consider a string to be an array of characters with which we can use write and read operations.
@@
 
-    Even if there are various criteria for methods, it is still necessary to determine how to get a library based on them.
+    Even if there are various criteria for functions, it is still necessary to determine how to get a library based on them.
 Therefore, we propose an algorithm that can be used for various (including not yet existing) object-oriented programming languages.
@@
 
-    It is necessary to set a criterion on the basis of which a decision will be made whether to add a method to the current set of methods.
+    It is necessary to set a criterion on the basis of which a decision will be made whether to add a function to the current set of functions.
 
@@
 
-    Now specifically about the algorithm on the basis of which the final set of methods will be obtained.
+    Now specifically about the algorithm on the basis of which the final set of functions will be obtained.
 
@@
         \item Set is initially empty.
-        \item Functions are considered in priority order, by default the most popular methods come first. If the method meets criterion 7.2, it is added to the set.
-        \item The second step is repeated until there are no unselected methods left.
-        \item In reverse order of priority the methods in the set are considered and those that don't meet criterion 7.2 are removed.
+        \item Functions are considered in priority order, by default the most popular functions come first. If the function meets criterion 7.2, it is added to the set.
+        \item The second step is repeated until there are no unselected functions left.
+        \item In reverse order of priority the functions in the set are considered and those that don't meet criterion 7.2 are removed.
     \end{enumerate}
@@
         \end{tabular}
-        \caption{String methods criteria}
+        \caption{String functions criteria}
         \label{tab:my_label}
@@
 
-    Based on these data, we have compiled our optimal library for string methods; the included methods are listed below.
+    Based on these data, we have compiled our optimal library for string functions; the included functions are listed below.
 
@@
 However, it is worth considering that a representation in the form of an oriented dependency graph would give more applied information.
-Because based on this graph, it would be less biased to construct a minimal set of string methods.
+Because based on this graph, it would be less biased to construct a minimal set of string functions.
 
-    However, it is not possible to represent the graph in this paper because the number of its edges would be too large (of the order of the square of the number of methods).
+    However, it is not possible to represent the graph in this paper because the number of its edges would be too large (of the order of the square of the number of functions).
 And such representation would lose any comprehensible visualization.
 
-    \subsection{Problems with method intersection}
+    \subsection{Problems with function intersection}
 
-    Earlier we mentioned the problem with popularity calculation for methods that have the same name, but are called on objects of different classes.
+    Earlier we mentioned the problem with popularity calculation for functions that have the same name, but are called on objects of different classes.
 
-    To solve this problem we can apply the extrapolation method here.
+    To solve this problem we can apply the extrapolation function here.
 
-    Note that this method does not show absolute accuracy; however, if the files to be analyzed are selected at random, the error decreases very much.
+    Note that this function does not show absolute accuracy; however, if the files to be analyzed are selected at random, the error decreases very much.
 

### 2022-08-19 article.tex
another class function problem simplified

@@
 
-    It is worth noting that functions which have had this problem are popular (note here that we mean functions for all classes, not specifically string functions), this we have obtained by making queries about the number of times they occur for code bases.
-For this reason, this data will not be counted in this article, but a function for solving this problem is given in the Discussion section.
+    It is worth noting that functions which have had this problem are popular, this we have obtained by making queries about the number of times they occur for code bases.
+For this reason, this data will not be counted in this article.
 

### 2022-08-22 article.tex
Unexpected advantage of immutability added
lang criteria added to used materials
"Why it’s not fixed yet by others?" added to introduction
introduction simplified

@@
 \usepackage[maxnames=1,minnames=1,maxbibnames=100,natbib=true,citestyle=authoryear,bibstyle=authoryear,doi=false,url=false,isbn=false,isbn=false]{biblatex}
-\addbibresource{main.bib}
 
@@
 
+\usepackage{rotating}
 \usepackage{debate}
@@
 
+    Most programming languages add functions to their string libraries without any limit on the number, for this reason there is no such research on this topic at the moment.
+
     This article aims to make a multivariate analysis of different parameters of string functions.
@@
 For this reason, this article does not consider all existing functions, but only those that meet some criteria.
-
-    An important factor for any function will be the frequency of its use in the code. In this article we will describe the algorithm, according to which we will evaluate this parameter.
-
-    Another important parameter that is investigated in this article is the number of uses of one function, inside (for realization) the others.
-This criterion allows us to identify important dependencies of some functions on others.
-
-    An algorithm to obtain the minimum set of required string functions will be created. This algorithm will be analyzed for susceptibility to bias, since it depends on the initial input data.
-
-    Also an important parameter for functions (in this case string functions) is their running time, so this article also considers this parameter.
-Since this is a complex analysis, the asymptotics of mutable and immutable string functions will be analyzed, as well as the asymptotics under full language immutability.
-
-    The article then discusses the results obtained and evaluates them. The accuracy of the obtained data is also evaluated. And a conclusion is made: which set of functions we took for our language.
+\hl{<- Transfer to method}
 
@@
 
+% \begin{sideways} \end{sideways}
+
         \end{tabular}
@@
 
-    \hl{todo}
+    An interesting fact was that, judging by the popularity of the use, the immutable methods are superior to the mutable ones.
 
@@
 
+    https://yegor256.github.io/plum/
+
     \hl{todo}

### 2022-08-22 article.tex
all research methods wrapped by one

@@
 
-    \section{Considered functions}
+    \section{Research Method}
+
+    \subsection{Considered functions}
 
@@
 
-    \section{Popularity of functions}
+    \subsection{Popularity of functions}
 
-    \subsection{Definition}
+    \subsubsection{Definition}
 
@@
 
-    \subsection{Search algorithm}
+    \subsubsection{Search algorithm}
 
@@
 
-    \section{Mutual usages}
+    \subsection{Mutual usages}
 
@@
 
-    \section{Asymptotics}
+    \subsection{Asymptotics}
 
-    \subsection{Mutable}
+    \subsubsection{Mutable}
 
@@
 
-    \subsection{Immutable}
+    \subsubsection{Immutable}
 
@@
 
-    \section{Finding the minimum set}
+    \subsection{Finding the minimum set}
 
-    \subsection{Necessity}
+    \subsubsection{Necessity}
 
@@
 
-    \subsection{Parameter setting}
+    \subsubsection{Criterion setting}
 
@@
 
-    \subsection{Algorithm}
+    \subsubsection{Algorithm}
 
@@
         \item Set is initially empty.
-        \item Functions are considered in priority order, by default the most popular functions come first. If the function meets criterion 7.2, it is added to the set.
+        \item Functions are considered in priority order, by default the most popular functions come first. If the function meets criterion 3.5.2, it is added to the set.
         \item The second step is repeated until there are no unselected functions left.
-        \item In reverse order of priority the functions in the set are considered and those that don't meet criterion 7.2 are removed.
+        \item In reverse order of priority the functions in the set are considered and those that don't meet criterion 3.5.2 are removed.
     \end{enumerate}

### 2022-08-22 article.tex
table moved to Appendices section
Acknowledgements added

@@
 
-    To avoid self-repeats, a summary list of the functions to be analyzed is presented in Section 8.
+    To avoid self-repeats, a summary list of the functions to be analyzed is presented in section \ref{table 1}.
 
@@
 
+    \label{criterion}
+
     It is necessary to set a criterion on the basis of which a decision will be made whether to add a function to the current set of functions.
@@
         \item Set is initially empty.
-        \item Functions are considered in priority order, by default the most popular functions come first. If the function meets criterion 3.5.2, it is added to the set.
+        \item Functions are considered in priority order, by default the most popular functions come first. If the function meets criterion \ref{criterion}, it is added to the set.
         \item The second step is repeated until there are no unselected functions left.
-        \item In reverse order of priority the functions in the set are considered and those that don't meet criterion 3.5.2 are removed.
+        \item In reverse order of priority the functions in the set are considered and those that don't meet criterion \ref{criterion} are removed.
     \end{enumerate}
@@
 
-    Below is a table with the results - metrics.
+    Below in section \ref{table 1} is a table with the results - metrics.
+
+    Based on these data, we have compiled our optimal library for string functions; the included functions are listed below.
+
+    \hl{todo}
+
+    \section{Discussion and analysis}
+
+    \subsection{Mutual usages presenting}
+
+    When we counted the Mutual usages parameter we used a numerical value.
+However, it is worth considering that a representation in the form of an oriented dependency graph would give more applied information.
+Because based on this graph, it would be less biased to construct a minimal set of string functions.
+
+    However, it is not possible to represent the graph in this paper because the number of its edges would be too large (of the order of the square of the number of functions).
+And such representation would lose any comprehensible visualization.
+
+    \subsection{Problems with function intersection}
+
+    Earlier we mentioned the problem with popularity calculation for functions that have the same name, but are called on objects of different classes.
+
+    To solve this problem we can apply the extrapolation function here.
+
+    Note that this function does not show absolute accuracy; however, if the files to be analyzed are selected at random, the error decreases very much.
+
+    In order to estimate the error it is necessary to take several similar samples and compare how different the results are.
+
+    \subsection{Unexpected advantage of immutability}
+
+    An interesting fact was that, judging by the popularity of the use, the immutable methods are superior to the mutable ones.
+
+    \section{Conclusion}\label{sec:conclusion}
+
+    \hl{todo}
+
+    \section{Acknowledgements}
+
+    The research was funded by Huawei Technologies Co. Ltd.
+
+    \section{References}
+
+    https://yegor256.github.io/plum/
+
+    \hl{todo}
+
+    \section{Appendices}
+
+    \label{table 1}
 
@@
 
-    Based on these data, we have compiled our optimal library for string functions; the included functions are listed below.
-
-    \hl{todo}
-
-    \section{Discussion and analysis}
-
-    \subsection{Mutual usages presenting}
-
-    When we counted the Mutual usages parameter we used a numerical value.
-However, it is worth considering that a representation in the form of an oriented dependency graph would give more applied information.
-Because based on this graph, it would be less biased to construct a minimal set of string functions.
-
-    However, it is not possible to represent the graph in this paper because the number of its edges would be too large (of the order of the square of the number of functions).
-And such representation would lose any comprehensible visualization.
-
-    \subsection{Problems with function intersection}
-
-    Earlier we mentioned the problem with popularity calculation for functions that have the same name, but are called on objects of different classes.
-
-    To solve this problem we can apply the extrapolation function here.
-
-    Note that this function does not show absolute accuracy; however, if the files to be analyzed are selected at random, the error decreases very much.
-
-    In order to estimate the error it is necessary to take several similar samples and compare how different the results are.
-
-    \subsection{Unexpected advantage of immutability}
-
-    An interesting fact was that, judging by the popularity of the use, the immutable methods are superior to the mutable ones.
-
-    \section{Conclusion}\label{sec:conclusion}
-
-    \hl{todo}
-
-    \section{Used materials}
-
-    https://yegor256.github.io/plum/
-
-    \hl{todo}
-
     \printbibliography

### 2022-08-22 article.tex
Considered functions redo

@@
 
-    We should keep in mind that the number of string functions in different programming languages is very large, and this number can grow, as we said before, without limitations.
-For this reason, this article does not consider all existing functions, but only those that meet some criteria.
-\hl{<- Transfer to method}
-
     \section{Related work}
@@
     In order to investigate functions, we have to make a list of functions to be investigated.
-For this purpose, programming languages such as Java, Python, C++, Ruby were chosen.
-They were chosen on the basis that they are quite popular, and they implement different paradigms (e.g.
+For this purpose, programming languages such as Java, Python, C++, Ruby, JavaScript, Go, C\#, Swift, PHP, Rust were chosen.
+They were chosen based on parameters such as the number of questions on StackOverflow, the number of repositories on GitHub with 100+ stars, and the TIOBE Index; and they implement different paradigms (e.g.
 strict and non-strict typing in C++ and Python respectively).
 
+    We should keep in mind that the number of string functions in different programming languages is very large, and this number can grow, as we said before, without limitations.
+For this reason, this article does not consider all existing functions, but only those that meet some criteria.
+
     A table with the list of different functions from standard string libraries for these languages has been compiled.
-For the analysis will be selected functions, which are presented at least in two programming languages (out of four presented).
-Since for the functions presented only in one language, we can conclude that they are used in too special or rare cases.
+For the analysis will be selected functions, which are presented at least in three programming languages (out of ten presented).
+Since for the functions presented only in one-two language, we can conclude that they are used in too special or rare cases.
 

### 2022-08-22 article.tex
clear method removed from table
lang columns added to table

@@
         \centering
-        \begin{tabular}{|c||c|c|c|c|}
+        \begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
             \hline
-            & Popularity & Mutual usages & Mutable O(?) & Immutable O(?) \\ \hline \hline
-            capitalize &  &  & 1 & 1 \\ \hline
+            & \begin{sideways}Java\end{sideways}
+            & \begin{sideways}Ruby\end{sideways}
+            & \begin{sideways}Python\end{sideways}
+            & \begin{sideways}C++\end{sideways}
+            & \begin{sideways}JavaScript\end{sideways}
+            & \begin{sideways}Go\end{sideways}
+            & \begin{sideways}C\#\end{sideways}
+            & \begin{sideways}Swift\end{sideways}
+            & \begin{sideways}PHP\end{sideways}
+            & \begin{sideways}Rust\end{sideways}
+            & \begin{sideways}Popularity\end{sideways}
+            & \begin{sideways}Mutual usages\end{sideways}
+            & \begin{sideways}Mutable O(?)\end{sideways}
+            & \begin{sideways}Immutable O(?)\end{sideways}
+            \\ \hline \hline
+            capitalize &  &  &  &  &  &  &  &  &  &  &  &  & 1 & 1 \\ \hline
 
-            char-at &  &  & 1 & 1 \\ \hline
+            char-at &  &  &  &  &  &  &  &  &  &  &  &  & 1 & 1 \\ \hline
 
-            compare &  &  & n & n \\ \hline
+            compare &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
 
-            compare-ignore-case &  &  &  & \\ \hline
+            compare-ignore-case &  &  &  &  &  &  &  &  &  &  &  &  &  & \\ \hline
 
-            concatenate &  &  & n & n \\ \hline
+            concatenate &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
 
-            containts &  &  & n & n \\ \hline
+            containts &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
 
-            count &  &  &  & \\ \hline
+            count &  &  &  &  &  &  &  &  &  &  &  &  &  & \\ \hline
 
-            ends-with &  &  & n & n \\ \hline
+            ends-with &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
 
-            equals &  &  & n & n \\ \hline
+            equals &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
 
-            find-first &  &  & n & n \\ \hline
+            find-first &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
 
-            find-last &  &  & n & n \\ \hline
+            find-last &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
 
-            format &  &  & n & n \\ \hline
+            format &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
 
-            hash &  &  & n & n \\ \hline
+            hash &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
 
-            insert &  &  & n & n \\ \hline
+            insert &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
 
-            is-alphabetic &  &  & n & n \\ \hline
+            is-alphabetic &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
 
-            is-empty &  &  & 1 & 1 \\ \hline
+            is-empty &  &  &  &  &  &  &  &  &  &  &  &  & 1 & 1 \\ \hline
 
-            is-hexadecimal &  &  & n & n \\ \hline
+            is-hexadecimal &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
 
-            is-int &  &  & n & n \\ \hline
+            is-int &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
 
-            is-lowercase &  &  & n & n \\ \hline
+            is-lowercase &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
 
-            is-uppercase &  &  & n & n \\ \hline
+            is-uppercase &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
 
-            is-whitespace &  &  & n & n \\ \hline
+            is-whitespace &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
 
-            join &  &  & n & n \\ \hline
+            join &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
 
-            length &  &  & 1 & 1 \\ \hline
+            length &  &  &  &  &  &  &  &  &  &  &  &  & 1 & 1 \\ \hline
 
-            matches-regexp &  &  & n & n \\ \hline
+            matches-regexp &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
 
-            partition &  &  & n & n \\ \hline
+            partition &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
 
-            repeat &  &  & n & n \\ \hline
+            repeat &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
 
-            replace-all &  &  & n & n \\ \hline
+            replace-all &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
 
-            replace-first  &  &  &  & \\ \hline
+            replace-first &  &  &  &  &  &  &  &  &  &   &  &  &  & \\ \hline
 
-            split &  &  & n & n \\ \hline
+            split &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
 
-            starts-with &  &  & n & n \\ \hline
+            starts-with &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
 
-            strip &  &  & n & n \\ \hline
+            strip &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
 
-            substring &  &  & n & 1 \\ \hline
+            substring &  &  &  &  &  &  &  &  &  &  &  &  & n & 1 \\ \hline
 
-            swap-case &  &  & n & n \\ \hline
+            swap-case &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
 
-            to-float &  &  & n & n \\ \hline
+            to-float &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
 
-            to-int &  &  & n & n \\ \hline
+            to-int &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
 
-            to-lowercase &  &  & n & n \\ \hline
+            to-lowercase &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
 
-            to-uppercase &  &  & n & n \\ \hline
+            to-uppercase &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
 
-            trim-left &  &  & n & n \\ \hline
+            trim-left &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
 
-            trim-right &  &  & n & n \\ \hline
+            trim-right &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
 
-            reverse &  &  & n & 1 \\ \hline
+            reverse &  &  &  &  &  &  &  &  &  &  &  &  & n & 1 \\ \hline
 
-            remove &  &  &  & \\ \hline
+            remove &  &  &  &  &  &  &  &  &  &  &  &  &  & \\ \hline
 
-            uncapitalize &  &  &  & \\ \hline
+            uncapitalize &  &  &  &  &  &  &  &  &  &  &  &  &  & \\ \hline
 
-            as-bytes &  &  &  & \\ \hline
+            as-bytes &  &  &  &  &  &  &  &  &  &  &  &  &  & \\ \hline
 
-            chop &  &  &  & \\ \hline
-
-            clear &  &  &  & \\ \hline
+            chop &  &  &  &  &  &  &  &  &  &  &  &  &  & \\ \hline
 

### 2022-08-24 article.tex
all functions are from standard libs

@@
 The standard library of string functions varies from language to language.
-Then in the case of creating a new language, you need to build your own library based on some criteria.
+When creating a new language, one needs to build their own library based on some criteria.
 However, the number of different functionality functions for strings that can be invented is at least countable (to put it simply - infinite).
@@
 
-    \section{Research Method}
+    \hl{add Section Metrics}
+
+    \section{Metrics}
 
@@
 strict and non-strict typing in C++ and Python respectively).
+\hl{move langs to results, add some part of bench table}
 
@@
 Since for the functions presented only in one-two language, we can conclude that they are used in too special or rare cases.
+\hl{using N, not 10}
 
@@
 This approach makes it possible to estimate the frequency of string functions usage exactly in the context of correlation with other string functions.
+\hl{remove all LET'S and YOU}
 
@@
 
-    The GitHub and Sourcegraph platforms were chosen to calculate the number of uses of the functions.
+    The GitHub and Sourcegraph platforms we choose to calculate the number of uses of the functions.
 This platform provides the ability to search for any words or phrases in all GitHub projects, as well as if necessary to specify other parameters.
@@
 
-    Below in section \ref{table 1} is a table with the results - metrics.
+    Below in section \ref{table 1} is a table with the results - metrics. It is important to note that these results take into account the methods of languages from their standard libraries.
 
@@
 
-    https://yegor256.github.io/plum/
+    https://yegor256.github.io/plum
 
-    \hl{todo}
+    https://github.com/search
+
+    https://sourcegraph.com/search
 

### 2022-08-24 article.tex
langs moved to results

@@
     In order to investigate functions, we have to make a list of functions to be investigated.
-For this purpose, programming languages such as Java, Python, C++, Ruby, JavaScript, Go, C\#, Swift, PHP, Rust were chosen.
+We chose N languages.
 They were chosen based on parameters such as the number of questions on StackOverflow, the number of repositories on GitHub with 100+ stars, and the TIOBE Index; and they implement different paradigms (e.g.
-strict and non-strict typing in C++ and Python respectively).
-\hl{move langs to results, add some part of bench table}
+strict and non-strict typing).
+\hl{add some part of bench table}
 
@@
     \section{Results}
+
+    After considering the criteria, we chose 10 programming languages. Languages such as Java, Python, C++, Ruby, JavaScript, Go, C\#, Swift, PHP, Rust were chosen.
 

### 2022-08-24 article.tex
using N, not 10 langs

@@
     A table with the list of different functions from standard string libraries for these languages has been compiled.
-For the analysis will be selected functions, which are presented at least in three programming languages (out of ten presented).
-Since for the functions presented only in one-two language, we can conclude that they are used in too special or rare cases.
-\hl{using N, not 10}
+For the analysis will be selected functions, which are presented at least in 30 percent of programming languages (out of N presented).
+Since for the functions presented less than 30 percent language, we can conclude that they are used in too special or rare cases.
 

### 2022-08-25 article.tex
new table style
table centering
part of bench table added
all let's and you removed

@@
 \usepackage[maxnames=1,minnames=1,maxbibnames=100,natbib=true,citestyle=authoryear,bibstyle=authoryear,doi=false,url=false,isbn=false,isbn=false]{biblatex}
-
-\usepackage[russian]{babel}
 
@@
 
-    Since popularity is a measurable parameter, let's calculate the number of uses of each string function (see below).
+    Since popularity is a measurable parameter, we calculated the number of uses of each string function (see below).
 Then we denote popularity as a percentage of the number of uses of a certain string function relative to the total number of uses of all string functions.
 This approach makes it possible to estimate the frequency of string functions usage exactly in the context of correlation with other string functions.
-\hl{remove all LET'S and YOU}
 
@@
 This platform provides the ability to search for any words or phrases in all GitHub projects, as well as if necessary to specify other parameters.
+However, we should keep in mind that asking for the number of repetitions of a certain word in the code will in some cases not give the right result, for a number of reasons.
 
-    However, you should take into account that asking for the number of times a certain word occurs in the code in certain cases will not give a correct result, there are a number of reasons for that.
-
-    \subsubsection{The word is a comment} \hl{}
+    \subsubsection{The word is a comment}
 
@@
 
-    \subsubsection{It's a another class function} \hl{}
+    \subsubsection{It's a another class function}
 
@@
 
-    For any function (in our case string functions) you can consider such a parameter as its use by other functions.
+    For any function (in our case string functions) we can consider such a parameter as its use by other functions.
 It is important because it is impossible to exclude a function from the library in case many other functions of the library use it.
@@
 
-    In order to define the asymptotics of the different string functions, let us define what a string is.
+    In order to define the asymptotics of the different string functions, we need to define what a string is.
 Since we are considering mutable strings, we consider a string to be an array of characters with which we can use write and read operations.
@@
     After considering the criteria, we chose 10 programming languages. Languages such as Java, Python, C++, Ruby, JavaScript, Go, C\#, Swift, PHP, Rust were chosen.
+
+    \begin{table}[h]
+        \begin{tabular}{llll}
+            \hline
+            & Questions
+            & Repositories 100+ stars
+            & TIOBE
+            \\ \hline
+
+            Python & 1911498 & 39308 & 1 \\
+
+            Java & 1833680 & 20216 & 3 \\
+
+            C++ & 758054 & 13609 & 4 \\ \hline
+        \end{tabular}
+        \caption{Part of the language criteria table}
+    \end{table}
 
@@
 
-    \begin{table*}[]
-        \centering
-        \begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
+    \begin{table*}
+        \begin{tabular}{lllllllllllllll}
             \hline
@@
             & \begin{sideways}Immutable O(?)\end{sideways}
-            \\ \hline \hline
-            capitalize &  &  &  &  &  &  &  &  &  &  &  &  & 1 & 1 \\ \hline
+            \\ \hline
 
-            char-at &  &  &  &  &  &  &  &  &  &  &  &  & 1 & 1 \\ \hline
+            capitalize &  &  &  &  &  &  &  &  &  &  &  &  & 1 & 1 \\
 
-            compare &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
+            char-at &  &  &  &  &  &  &  &  &  &  &  &  & 1 & 1 \\
 
-            compare-ignore-case &  &  &  &  &  &  &  &  &  &  &  &  &  & \\ \hline
+            compare &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
 
-            concatenate &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
+            compare-ignore-case &  &  &  &  &  &  &  &  &  &  &  &  &  & \\
 
-            containts &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
+            concatenate &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
 
-            count &  &  &  &  &  &  &  &  &  &  &  &  &  & \\ \hline
+            containts &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
 
-            ends-with &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
+            count &  &  &  &  &  &  &  &  &  &  &  &  &  & \\
 
-            equals &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
+            ends-with &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
 
-            find-first &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
+            equals &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
 
-            find-last &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
+            find-first &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
 
-            format &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
+            find-last &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
 
-            hash &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
+            format &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
 
-            insert &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
+            hash &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
 
-            is-alphabetic &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
+            insert &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
 
-            is-empty &  &  &  &  &  &  &  &  &  &  &  &  & 1 & 1 \\ \hline
+            is-alphabetic &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
 
-            is-hexadecimal &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
+            is-empty &  &  &  &  &  &  &  &  &  &  &  &  & 1 & 1 \\
 
-            is-int &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
+            is-hexadecimal &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
 
-            is-lowercase &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
+            is-int &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
 
-            is-uppercase &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
+            is-lowercase &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
 
-            is-whitespace &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
+            is-uppercase &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
 
-            join &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
+            is-whitespace &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
 
-            length &  &  &  &  &  &  &  &  &  &  &  &  & 1 & 1 \\ \hline
+            join &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
 
-            matches-regexp &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
+            length &  &  &  &  &  &  &  &  &  &  &  &  & 1 & 1 \\
 
-            partition &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
+            matches-regexp &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
 
-            repeat &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
+            partition &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
 
-            replace-all &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
+            repeat &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
 
-            replace-first &  &  &  &  &  &  &  &  &  &   &  &  &  & \\ \hline
+            replace-all &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
 
-            split &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
+            replace-first &  &  &  &  &  &  &  &  &  &   &  &  &  & \\
 
-            starts-with &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
+            split &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
 
-            strip &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
+            starts-with &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
 
-            substring &  &  &  &  &  &  &  &  &  &  &  &  & n & 1 \\ \hline
+            strip &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
 
-            swap-case &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
+            substring &  &  &  &  &  &  &  &  &  &  &  &  & n & 1 \\
 
-            to-float &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
+            swap-case &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
 
-            to-int &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
+            to-float &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
 
-            to-lowercase &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
+            to-int &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
 
-            to-uppercase &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
+            to-lowercase &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
 
-            trim-left &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
+            to-uppercase &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
 
-            trim-right &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline
+            trim-left &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
 
-            reverse &  &  &  &  &  &  &  &  &  &  &  &  & n & 1 \\ \hline
+            trim-right &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
 
-            remove &  &  &  &  &  &  &  &  &  &  &  &  &  & \\ \hline
+            reverse &  &  &  &  &  &  &  &  &  &  &  &  & n & 1 \\
 
-            uncapitalize &  &  &  &  &  &  &  &  &  &  &  &  &  & \\ \hline
+            remove &  &  &  &  &  &  &  &  &  &  &  &  &  & \\
 
-            as-bytes &  &  &  &  &  &  &  &  &  &  &  &  &  & \\ \hline
+            uncapitalize &  &  &  &  &  &  &  &  &  &  &  &  &  & \\
+
+            as-bytes &  &  &  &  &  &  &  &  &  &  &  &  &  & \\
 
             chop &  &  &  &  &  &  &  &  &  &  &  &  &  & \\ \hline
-
-% \begin{sideways} \end{sideways}
-
         \end{tabular}

### 2022-08-28 article.tex
method section created
results starting changed

@@
 \usepackage{debate}
+\usepackage{tabularx}
 \usepackage{ffcode}
@@
 
-    \hl{add Section Metrics}
-
     \section{Metrics}
-
-    \subsection{Considered functions}
-
-    In order to investigate functions, we have to make a list of functions to be investigated.
-We chose N languages.
-They were chosen based on parameters such as the number of questions on StackOverflow, the number of repositories on GitHub with 100+ stars, and the TIOBE Index; and they implement different paradigms (e.g.
-strict and non-strict typing).
-\hl{add some part of bench table}
-
-    We should keep in mind that the number of string functions in different programming languages is very large, and this number can grow, as we said before, without limitations.
-For this reason, this article does not consider all existing functions, but only those that meet some criteria.
-
-    A table with the list of different functions from standard string libraries for these languages has been compiled.
-For the analysis will be selected functions, which are presented at least in 30 percent of programming languages (out of N presented).
-Since for the functions presented less than 30 percent language, we can conclude that they are used in too special or rare cases.
-
-    To avoid self-repeats, a summary list of the functions to be analyzed is presented in section \ref{table 1}.
 
@@
 However, we should keep in mind that asking for the number of repetitions of a certain word in the code will in some cases not give the right result, for a number of reasons.
+\hl{maybe move platforms names to Method Section}
 
@@
     For some words, it is more common for them to appear in files as names/comments/inside strings rather than as called functions.
-Since the article deals with the use of string functions for object-oriented languages, and they use dot notation, it will be more efficient to make queries like .<function name>, instead of <function name>.
+Since the article deals with the use of string functions for object-oriented languages, and they use dot notation, it will be more efficient to make queries like \textit{.function}, instead of \textit{function}.
+\hl{to discussion}
 
@@
     In this kind of analysis, for some functions there is a problem that it is not clear which class of objects has which function.
-For example, the contains function is present in string as well as in most collections.
+For example, the \textit{contains} function is present in string as well as in most collections.
 
@@
 For this reason, this data will not be counted in this article.
+\hl{to discussion}
 
@@
 
-    For any function (in our case string functions) we can consider such a parameter as its use by other functions.
+    For any function we can consider such a parameter as its use by other functions.
 It is important because it is impossible to exclude a function from the library in case many other functions of the library use it.
@@
 
-    \subsection{Finding the minimum set}
+    \subsection{The minimum set}
 
@@
 
+    \hl{maybe move algorithm to Section method}
+
+    \section{Method}
+
+    In order to investigate functions, we will make a list of functions to be investigated.
+We will choose N languages.
+They were chosen based on parameters such as the number of questions on StackOverflow, the number of repositories on GitHub with 100+ stars, and the TIOBE Index; and they implement different paradigms (e.g.
+strict and non-strict typing).
+    We should keep in mind that the number of string functions in different programming languages is very large, and this number can grow, as we said before, without limitations.
+For this reason, this article does not consider all existing functions, but only those that meet some criteria.
+
+    A table with the list of different functions from standard string libraries for these languages has been compiled.
+For the analysis will be selected functions, which are presented at least in 30 percent of programming languages (out of N presented).
+Since for the functions presented less than 30 percent language, we can conclude that they are used in too special or rare cases.
+
     \section{Results}
 
-    After considering the criteria, we chose 10 programming languages. Languages such as Java, Python, C++, Ruby, JavaScript, Go, C\#, Swift, PHP, Rust were chosen.
+    Below are the 10 programming languages we have chosen and their criteria.
+
+    \hl{Java, Python, C++, Ruby, JavaScript, Go, C\#, Swift, PHP, Rust were chosen.}
 
@@
 
-            char-at &  &  &  &  &  &  &  &  &  &  &  &  & 1 & 1 \\
+            Get \textbf{char-at} a given position &  &  &  &  &  &  &  &  &  &  &  &  & 1 & 1 \\
 

### 2022-08-28 article.tex
refs changed
table for methods existing separated

@@
 
-    Below in section \ref{table 1} is a table with the results - metrics. It is important to note that these results take into account the methods of languages from their standard libraries.
+    Below in section \ref{tab:my_label} is a table with the results - metrics. It is important to note that these results take into account the methods of languages from their standard libraries.
 
@@
 
-    \label{table 1}
+    \subsection{The table of functions in languages}
 
     \begin{table*}
-        \begin{tabular}{lllllllllllllll}
+        \begin{tabular}{lllllllllll}
             \hline
@@
             & \begin{sideways}Rust\end{sideways}
-            & \begin{sideways}Popularity\end{sideways}
-            & \begin{sideways}Mutual usages\end{sideways}
-            & \begin{sideways}Mutable O(?)\end{sideways}
-            & \begin{sideways}Immutable O(?)\end{sideways}
             \\ \hline
 
-            capitalize &  &  &  &  &  &  &  &  &  &  &  &  & 1 & 1 \\
+            capitalize &  &  &  &  &  & &  &  & 1 & 1 \\
 
-            Get \textbf{char-at} a given position &  &  &  &  &  &  &  &  &  &  &  &  & 1 & 1 \\
+            Get \textbf{char-at} a given position &  &  &  &  &  & &  &  & 1 & 1 \\
 
-            compare &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
+            compare &  &  &  &  &  & &  &  & n & n \\
 
-            compare-ignore-case &  &  &  &  &  &  &  &  &  &  &  &  &  & \\
+            compare-ignore-case &  &  &  &  &  & &  &  &  & \\
 
-            concatenate &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
+            concatenate &  &  &  &  &  & &  &  & n & n \\
 
-            containts &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
+            containts &  &  &  &  &  & &  &  & n & n \\
 
-            count &  &  &  &  &  &  &  &  &  &  &  &  &  & \\
+            count &  &  &  &  &  & &  &  &  & \\
 
-            ends-with &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
+            ends-with &  &  &  &  &  & &  &  & n & n \\
 
-            equals &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
+            equals &  &  &  &  &  & &  &  & n & n \\
 
-            find-first &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
+            find-first &  &  &  &  &  & &  &  & n & n \\
 
-            find-last &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
+            find-last &  &  &  &  &  & &  &  & n & n \\
 
-            format &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
+            format &  &  &  &  &  & &  &  & n & n \\
 
-            hash &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
+            hash &  &  &  &  &  & &  &  & n & n \\
 
-            insert &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
+            insert &  &  &  &  &  & &  &  & n & n \\
 
-            is-alphabetic &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
+            is-alphabetic &  &  &  &  &  & &  &  & n & n \\
 
-            is-empty &  &  &  &  &  &  &  &  &  &  &  &  & 1 & 1 \\
+            is-empty &  &  &  &  &  & &  &  & 1 & 1 \\
 
-            is-hexadecimal &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
+            is-hexadecimal &  &  &  &  &  & &  &  & n & n \\
 
-            is-int &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
+            is-int &  &  &  &  &  & &  &  & n & n \\
 
-            is-lowercase &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
+            is-lowercase &  &  &  &  &  & &  &  & n & n \\
 
-            is-uppercase &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
+            is-uppercase &  &  &  &  &  & &  &  & n & n \\
 
-            is-whitespace &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
+            is-whitespace &  &  &  &  &  & &  &  & n & n \\
 
-            join &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
+            join &  &  &  &  &  & &  &  & n & n \\
 
-            length &  &  &  &  &  &  &  &  &  &  &  &  & 1 & 1 \\
+            length &  &  &  &  &  & &  &  & 1 & 1 \\
 
-            matches-regexp &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
+            matches-regexp &  &  &  &  &  & &  &  & n & n \\
 
-            partition &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
+            partition &  &  &  &  &  & &  &  & n & n \\
 
-            repeat &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
+            repeat &  &  &  &  &  & &  &  & n & n \\
 
-            replace-all &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
+            replace-all &  &  &  &  &  & &  &  & n & n \\
 
-            replace-first &  &  &  &  &  &  &  &  &  &   &  &  &  & \\
+            replace-first &  &  &  &  &  &  &  &  &  & \\
 
-            split &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
+            split &  &  &  &  &  & &  &  & n & n \\
 
-            starts-with &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
+            starts-with &  &  &  &  &  & &  &  & n & n \\
 
-            strip &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
+            strip &  &  &  &  &  & &  &  & n & n \\
 
-            substring &  &  &  &  &  &  &  &  &  &  &  &  & n & 1 \\
+            substring &  &  &  &  &  & &  &  & n & 1 \\
 
-            swap-case &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
+            swap-case &  &  &  &  &  & &  &  & n & n \\
 
-            to-float &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
+            to-float &  &  &  &  &  & &  &  & n & n \\
 
-            to-int &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
+            to-int &  &  &  &  &  & &  &  & n & n \\
 
-            to-lowercase &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
+            to-lowercase &  &  &  &  &  & &  &  & n & n \\
 
-            to-uppercase &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
+            to-uppercase &  &  &  &  &  & &  &  & n & n \\
 
-            trim-left &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
+            trim-left &  &  &  &  &  & &  &  & n & n \\
 
-            trim-right &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\
+            trim-right &  &  &  &  &  & &  &  & n & n \\
 
-            reverse &  &  &  &  &  &  &  &  &  &  &  &  & n & 1 \\
+            reverse &  &  &  &  &  & &  &  & n & 1 \\
 
-            remove &  &  &  &  &  &  &  &  &  &  &  &  &  & \\
+            remove &  &  &  &  &  & &  &  &  & \\
 
-            uncapitalize &  &  &  &  &  &  &  &  &  &  &  &  &  & \\
+            uncapitalize &  &  &  &  &  & &  &  &  & \\
 
-            as-bytes &  &  &  &  &  &  &  &  &  &  &  &  &  & \\
+            as-bytes &  &  &  &  &  & &  &  &  & \\
 
-            chop &  &  &  &  &  &  &  &  &  &  &  &  &  & \\ \hline
+            chop &  &  &  &  &  & &  &  &  & \\ \hline
         \end{tabular}

### 2022-08-28 article.tex
all java functions added

@@
 
-    Below in section \ref{tab:my_label} is a table with the results - metrics. It is important to note that these results take into account the methods of languages from their standard libraries.
+    Below in section \ref{tab:my_label} is a table with the results - metrics. It is important to note that these results take into account the functions of languages from their standard libraries.
 
@@
 
-    An interesting fact was that, judging by the popularity of the use, the immutable methods are superior to the mutable ones.
+    An interesting fact was that, judging by the popularity of the use, the immutable functions are superior to the mutable ones.
 
@@
 
+    \subsection{String function metrics}
+
+    \hl{todo}
+
+    \subsection{String functions of standard libraries}
+
+    \textbf{Java}: charAt, codePointAt, codePointBefore, codePointCount, compareTo, compareToIgnoreCase, concat, contains, contentEquals, copyValueOf, endsWith, equals, equalsIgnoreCase, format, getBytes, getChars, hashCode, indexOf, intern, isEmpty, length, lastIndexOf, length, matches, offsetByCodePoints, regionMatches, replace, replaceAll, replaceFirst, split, startsWith, subSequence, substring, toCharArray, toLowerCase, toString, toUpperCase, trim, valueOf.
+
     \printbibliography

### 2022-08-28 article.tex
all ruby functions added

@@
 
+    \textbf{Ruby}: new, try\_convert, \%, *, +, +@, -@, <<, <=>, ==, ===, =~, [], []=, ascii\_only\?, b, bytes, bytesize, byteslice, capitalize, capitalize!, casecmp, casecmp\?, center, chars, chomp, chomp!, chop, chop!, chr, clear, codepoints, concat, count, crypt, delete, delete!, delete\_prefix, delete\_prefix!, delete\_suffix, delete\_suffix!, downcase, downcase!, dump, each\_byte, each\_char, each\_codepoint, each\_grapheme\_cluster, each\_line, empty\?, encode, encode!, encoding, end\_with\?, eql\?, force\_encoding, freeze, getbyte, grapheme\_clusters, gsub, gsub!, hash, hex, include\?, index, initialize\_copy, insert, inspect, intern, length, lines, ljust, lstrip, lstrip!, match, match\?, next, next!, oct, ord, partition, prepend, replace, reverse, reverse!, rindex, rjust, rpartition, rstrip, rstrip!, scan, scrub, scrub!, setbyte, size, slice, slice!, split, squeeze, squeeze!, start\_with\?, strip, strip!, sub, sub!, succ, succ!, sum, swapcase, swapcase!, to\_c, to\_f, to\_i, to\_r, to\_s, to\_str, to\_sym, tr, tr!, tr\_s, tr\_s!, undump, unicode\_normalize, unicode\_normalize!, unicode\_normalized\?, unpack, unpack1, upcase, upcase!, upto, valid\_encoding\?.
+
     \printbibliography

### 2022-08-28 article.tex
all python functions added

@@
 
+    \textbf{Python}: capitalize, casefold, center, count, encode, endswith, expandtabs, find, format, format\_map, index, isalnum, isalpha, isascii, isdecimal, isdigit, isidentifier, islower, isnumeric, isprintable, isspace, istitle, isupper, join, ljust, lower, lstrip, maketrans, partition, replace, rfind, rindex, rjust, rpartition, rsplit, rstrip, split, splitlines, startswith, strip, swapcase, title, translate, upper, zfill.
+
     \printbibliography

### 2022-08-28 article.tex
all c++ functions added

@@
 
+    \textbf{C++}: append, assign, at, back, begin, c\_str, capacity, cbegin, cend, clear, compare, copy, crbegin, crend, data, empty, end, erase, find, find\_first\_not\_of, find\_first\_of, find\_last\_not\_of, find\_last\_of, front, get\_allocator, insert, length, max\_size, operator\[\], operator+=, operator=, pop\_back, push\_back, rbegin, rend, replace, reserve, resize, rfind, shrink\_to\_fit, size, substr, swap.
+
     \printbibliography

### 2022-08-28 article.tex
all c++ functions fixed

--- 2022-08-28 article.tex
@@
 
+    \textbf{C++}: append, assign, at, back, begin, c\_str, capacity, cbegin, cend, clear, compare, copy, crbegin, crend, data, empty, end, erase, find, find\_first\_not\_of, find\_first\_of, find\_last\_not\_of, find\_last\_of, front, get\_allocator, insert, length, max\_size, operator[], operator+=, operator=, pop\_back, push\_back, rbegin, rend, replace, reserve, resize, rfind, shrink\_to\_fit, size, substr, swap.
+
     \printbibliography

### 2022-08-28 article.tex
all ruby functions fixed

@@
 
-    \textbf{Ruby}: new, try\_convert, \%, *, +, +@, -@, <<, <=>, ==, ===, =~, [], []=, ascii\_only\?, b, bytes, bytesize, byteslice, capitalize, capitalize!, casecmp, casecmp\?, center, chars, chomp, chomp!, chop, chop!, chr, clear, codepoints, concat, count, crypt, delete, delete!, delete\_prefix, delete\_prefix!, delete\_suffix, delete\_suffix!, downcase, downcase!, dump, each\_byte, each\_char, each\_codepoint, each\_grapheme\_cluster, each\_line, empty\?, encode, encode!, encoding, end\_with\?, eql\?, force\_encoding, freeze, getbyte, grapheme\_clusters, gsub, gsub!, hash, hex, include\?, index, initialize\_copy, insert, inspect, intern, length, lines, ljust, lstrip, lstrip!, match, match\?, next, next!, oct, ord, partition, prepend, replace, reverse, reverse!, rindex, rjust, rpartition, rstrip, rstrip!, scan, scrub, scrub!, setbyte, size, slice, slice!, split, squeeze, squeeze!, start\_with\?, strip, strip!, sub, sub!, succ, succ!, sum, swapcase, swapcase!, to\_c, to\_f, to\_i, to\_r, to\_s, to\_str, to\_sym, tr, tr!, tr\_s, tr\_s!, undump, unicode\_normalize, unicode\_normalize!, unicode\_normalized\?, unpack, unpack1, upcase, upcase!, upto, valid\_encoding\?.
+    \textbf{Ruby}: new, try\_convert, \%, *, +, +@, -@, <<, <=>, ==, ===, =\~, [], []=, ascii\_only?, b, bytes, bytesize, byteslice, capitalize, capitalize!, casecmp, casecmp?, center, chars, chomp, chomp!, chop, chop!, chr, clear, codepoints, concat, count, crypt, delete, delete!, delete\_prefix, delete\_prefix!, delete\_suffix, delete\_suffix!, downcase, downcase!, dump, each\_byte, each\_char, each\_codepoint, each\_grapheme\_cluster, each\_line, empty?, encode, encode!, encoding, end\_with?, eql?, force\_encoding, freeze, getbyte, grapheme\_clusters, gsub, gsub!, hash, hex, include?, index, initialize\_copy, insert, inspect, intern, length, lines, ljust, lstrip, lstrip!, match, match?, next, next!, oct, ord, partition, prepend, replace, reverse, reverse!, rindex, rjust, rpartition, rstrip, rstrip!, scan, scrub, scrub!, setbyte, size, slice, slice!, split, squeeze, squeeze!, start\_with?, strip, strip!, sub, sub!, succ, succ!, sum, swapcase, swapcase!, to\_c, to\_f, to\_i, to\_r, to\_s, to\_str, to\_sym, tr, tr!, tr\_s, tr\_s!, undump, unicode\_normalize, unicode\_normalize!, unicode\_normalized?, unpack, unpack1, upcase, upcase!, upto, valid\_encoding?.
 

### 2022-08-28 article.tex
all js functions added

@@
 
-    \subsection{The table of functions in languages}
-
     \begin{table*}
@@
         \end{tabular}
-        \caption{String functions criteria}
+        \caption{String functions existing in languages}
         \label{tab:my_label}
@@
 
-    \subsection{String function metrics}
+    \hl{todo String function metrics table}
 
-    \hl{todo}
-
-    \subsection{String functions of standard libraries}
+    Below we have a list of all string functions from the standard libraries of the specified languages.
 
@@
 
+    \textbf{JavaScript}: charAt, charCodeAt, codePointAt, concat, constructor, endsWith, fromCharCode, includes, indexOf, lastIndexOf, length, localeCompare, match, prototype, repeat, replace, search, slice, split, startsWith, substr, substring, toLocaleLowerCase, toLocaleUpperCase, toLowerCase, toString, toUpperCase, trim, valueOf.
+
     \printbibliography

### 2022-08-28 article.tex
all js functions added
all go functions added

@@
 
+    \textbf{Go}: Clone, Compare, Contains, ContainsAny, ContainsRune, Count, Cut, EqualFold, Fields, FieldsFunc, func, HasPrefix, HasSuffix, Index, IndexAny, IndexByte, IndexFunc, func, IndexRune, Join, LastIndex, LastIndexAny, LastIndexByte, LastIndexFunc, func, Map, func, Repeat, Replace, ReplaceAll, Split, SplitAfter, SplitAfterN, SplitN, Title, ToLower, ToLowerSpecial, ToTitle, ToTitleSpecial, ToUpper, ToUpperSpecial, ToValidUTF8, Trim, TrimFunc, func, TrimLeft, TrimLeftFunc, func, TrimPrefix, TrimRight, TrimRightFunc, func, TrimSpace, TrimSuffix.
+
+    \textbf{C#}:
+
+    \textbf{Swift}:
+
+    \textbf{PHP}:
+
+    \textbf{Rust}:
+
     \printbibliography

### 2022-08-28 article.tex
all csharp functions added
all php functions added

@@
 
+    \hl{todo String function metrics table}
+
+    Below we have a list of all string functions from the standard libraries of the specified languages.
+
+    \textbf{Java}: charAt, codePointAt, codePointBefore, codePointCount, compareTo, compareToIgnoreCase, concat, contains, contentEquals, copyValueOf, endsWith, equals, equalsIgnoreCase, format, getBytes, getChars, hashCode, indexOf, intern, isEmpty, length, lastIndexOf, length, matches, offsetByCodePoints, regionMatches, replace, replaceAll, replaceFirst, split, startsWith, subSequence, substring, toCharArray, toLowerCase, toString, toUpperCase, trim, valueOf.
+
+    \textbf{Ruby}: new, try\_convert, \%, *, +, +@, -@, <<, <=>, ==, ===, =\~, [], []=, ascii\_only?, b, bytes, bytesize, byteslice, capitalize, capitalize!, casecmp, casecmp?, center, chars, chomp, chomp!, chop, chop!, chr, clear, codepoints, concat, count, crypt, delete, delete!, delete\_prefix, delete\_prefix!, delete\_suffix, delete\_suffix!, downcase, downcase!, dump, each\_byte, each\_char, each\_codepoint, \\ each\_grapheme\_cluster, each\_line, empty?, encode, encode!, encoding, end\_with?, eql?, force\_encoding, freeze, getbyte, grapheme\_clusters, gsub, gsub!, hash, hex, include?, index, initialize\_copy, insert, inspect, intern, length, lines, ljust, lstrip, lstrip!, match, match?, next, next!, oct, ord, partition, prepend, replace, reverse, reverse!, rindex, rjust, rpartition, rstrip, rstrip!, scan, scrub, scrub!, setbyte, size, slice, slice!, split, squeeze, squeeze!, start\_with?, strip, strip!, sub, sub!, succ, succ!, sum, swapcase, swapcase!, to\_c, to\_f, to\_i, to\_r, to\_s, to\_str, to\_sym, tr, tr!, tr\_s, tr\_s!, undump, unicode\_normalize, unicode\_normalize!, unicode\_normalized?, unpack, unpack1, upcase, upcase!, upto, valid\_encoding?.
+
+    \textbf{Python}: capitalize, casefold, center, count, encode, endswith, expandtabs, find, format, format\_map, index, isalnum, isalpha, isascii, isdecimal, isdigit, isidentifier, islower, isnumeric, isprintable, isspace, istitle, isupper, join, ljust, lower, lstrip, maketrans, partition, replace, rfind, rindex, rjust, rpartition, rsplit, rstrip, split, splitlines, startswith, strip, swapcase, title, translate, upper, zfill.
+
+    \textbf{C++}: append, assign, at, back, begin, c\_str, capacity, cbegin, cend, clear, compare, copy, crbegin, crend, data, empty, end, erase, find, find\_first\_not\_of, find\_first\_of, find\_last\_not\_of, find\_last\_of, front, get\_allocator, insert, length, max\_size, operator[], operator+=, operator=, pop\_back, push\_back, rbegin, rend, replace, reserve, resize, rfind, shrink\_to\_fit, size, substr, swap.
+
+    \textbf{JavaScript}: charAt, charCodeAt, codePointAt, concat, constructor, endsWith, fromCharCode, includes, indexOf, lastIndexOf, length, localeCompare, match, prototype, repeat, replace, search, slice, split, startsWith, substr, substring, toLocaleLowerCase, toLocaleUpperCase, toLowerCase, toString, toUpperCase, trim, valueOf.
+
+    \textbf{Go}: Clone, Compare, Contains, ContainsAny, ContainsRune, Count, Cut, EqualFold, Fields, FieldsFunc, func, HasPrefix, HasSuffix, Index, IndexAny, IndexByte, IndexFunc, func, IndexRune, Join, LastIndex, LastIndexAny, LastIndexByte, LastIndexFunc, func, Map, func, Repeat, Replace, ReplaceAll, Split, SplitAfter, SplitAfterN, SplitN, Title, ToLower, ToLowerSpecial, ToTitle, ToTitleSpecial, ToUpper, ToUpperSpecial, ToValidUTF8, Trim, TrimFunc, func, TrimLeft, TrimLeftFunc, func, TrimPrefix, TrimRight, TrimRightFunc, func, TrimSpace, TrimSuffix.
+
+    \textbf{C\#}:
+
+    Clone, CompareTo, Contains, EndsWith, Equals, GetHashCode, GetType, GetTypeCode, IndexOf, ToLower, ToUpper, Insert, IsNormalized, LastIndexOf, Remove, Replace, Split, StartsWith, Substring, ToCharArray, Trim.
+
+    \textbf{Swift}:
+
+    \textbf{PHP}: addcslashes, addslashes, bin2hex, chop, chr, chunk\_split, convert\_cyr\_string, convert\_uudecode, convert\_uuencode, count\_chars, crc32, crypt, echo, explode, fprint, get\_html\_translation\_table, hebrev, hebrevc, hex2bin, html\_entity\_decode, htmlentities, htmlspecialchars\_decode, htmlspecialchars, implode, join, lcfirst, levenshtein, localeconv, ltrim, md5, md5\_file, metaphone, money\_format, nl\_langinfo, nl2br, number\_format, ord, parse\_str, print, printf, quoted\_printable\_decode, quoted\_printable\_encode, quotemeta, rtrim, setlocale, sha1, sha1\_file, similar\_text, soundex, sprintf, sscanf, str\_getcsv, str\_ireplace, str\_pad, str\_repeat, str\_replace, str\_rot13, str\_shuffle, str\_split, str\_word\_count, strcasecmp, strchr, strcmp, strcoll, strcspn, strip\_tags, stripcslashes, stripslashes, stripos, stristr, strlen, strnatcasecmp, strnatcmp, strncasecmp, strncmp, strpbrk, strpos, strrchr, strrev, strripos, strrpos, strspn, strstr, strtok, strtolower, strtoupper, strtr, substr, substr\_compare, substr\_count, substr\_replace, trim, ucfirst, ucwords, vfprintf, vprintf, vsprintf, wordwrap.
+
+    \textbf{Rust}:
+
     \begin{table*}
@@
 
-    \hl{todo String function metrics table}
-
-    Below we have a list of all string functions from the standard libraries of the specified languages.
-
-    \textbf{Java}: charAt, codePointAt, codePointBefore, codePointCount, compareTo, compareToIgnoreCase, concat, contains, contentEquals, copyValueOf, endsWith, equals, equalsIgnoreCase, format, getBytes, getChars, hashCode, indexOf, intern, isEmpty, length, lastIndexOf, length, matches, offsetByCodePoints, regionMatches, replace, replaceAll, replaceFirst, split, startsWith, subSequence, substring, toCharArray, toLowerCase, toString, toUpperCase, trim, valueOf.
-
-    \textbf{Ruby}: new, try\_convert, \%, *, +, +@, -@, <<, <=>, ==, ===, =\~, [], []=, ascii\_only?, b, bytes, bytesize, byteslice, capitalize, capitalize!, casecmp, casecmp?, center, chars, chomp, chomp!, chop, chop!, chr, clear, codepoints, concat, count, crypt, delete, delete!, delete\_prefix, delete\_prefix!, delete\_suffix, delete\_suffix!, downcase, downcase!, dump, each\_byte, each\_char, each\_codepoint, each\_grapheme\_cluster, each\_line, empty?, encode, encode!, encoding, end\_with?, eql?, force\_encoding, freeze, getbyte, grapheme\_clusters, gsub, gsub!, hash, hex, include?, index, initialize\_copy, insert, inspect, intern, length, lines, ljust, lstrip, lstrip!, match, match?, next, next!, oct, ord, partition, prepend, replace, reverse, reverse!, rindex, rjust, rpartition, rstrip, rstrip!, scan, scrub, scrub!, setbyte, size, slice, slice!, split, squeeze, squeeze!, start\_with?, strip, strip!, sub, sub!, succ, succ!, sum, swapcase, swapcase!, to\_c, to\_f, to\_i, to\_r, to\_s, to\_str, to\_sym, tr, tr!, tr\_s, tr\_s!, undump, unicode\_normalize, unicode\_normalize!, unicode\_normalized?, unpack, unpack1, upcase, upcase!, upto, valid\_encoding?.
-
-    \textbf{Python}: capitalize, casefold, center, count, encode, endswith, expandtabs, find, format, format\_map, index, isalnum, isalpha, isascii, isdecimal, isdigit, isidentifier, islower, isnumeric, isprintable, isspace, istitle, isupper, join, ljust, lower, lstrip, maketrans, partition, replace, rfind, rindex, rjust, rpartition, rsplit, rstrip, split, splitlines, startswith, strip, swapcase, title, translate, upper, zfill.
-
-    \textbf{C++}: append, assign, at, back, begin, c\_str, capacity, cbegin, cend, clear, compare, copy, crbegin, crend, data, empty, end, erase, find, find\_first\_not\_of, find\_first\_of, find\_last\_not\_of, find\_last\_of, front, get\_allocator, insert, length, max\_size, operator[], operator+=, operator=, pop\_back, push\_back, rbegin, rend, replace, reserve, resize, rfind, shrink\_to\_fit, size, substr, swap.
-
-    \textbf{JavaScript}: charAt, charCodeAt, codePointAt, concat, constructor, endsWith, fromCharCode, includes, indexOf, lastIndexOf, length, localeCompare, match, prototype, repeat, replace, search, slice, split, startsWith, substr, substring, toLocaleLowerCase, toLocaleUpperCase, toLowerCase, toString, toUpperCase, trim, valueOf.
-
-    \textbf{Go}: Clone, Compare, Contains, ContainsAny, ContainsRune, Count, Cut, EqualFold, Fields, FieldsFunc, func, HasPrefix, HasSuffix, Index, IndexAny, IndexByte, IndexFunc, func, IndexRune, Join, LastIndex, LastIndexAny, LastIndexByte, LastIndexFunc, func, Map, func, Repeat, Replace, ReplaceAll, Split, SplitAfter, SplitAfterN, SplitN, Title, ToLower, ToLowerSpecial, ToTitle, ToTitleSpecial, ToUpper, ToUpperSpecial, ToValidUTF8, Trim, TrimFunc, func, TrimLeft, TrimLeftFunc, func, TrimPrefix, TrimRight, TrimRightFunc, func, TrimSpace, TrimSuffix.
-
-    \textbf{C#}:
-
-    \textbf{Swift}:
-
-    \textbf{PHP}:
-
-    \textbf{Rust}:
-
     \printbibliography

### 2022-08-28 article.tex
all rust functions added

@@
 
-    \textbf{Rust}:
+    \textbf{Rust}: new, with\_capacity, from\_utf8, from\_utf8\_lossy, from\_utf16, from\_utf16\_lossy, from\_raw\_parts, from\_utf8\_unchecked, into\_bytes, as\_str, as\_mut\_str, push\_str, capacity, reserve, reserve\_exact, try\_reserve, try\_reserve\_exact, shrink\_to\_fit, shrink\_to, push, as\_bytes, truncate, pop, remove, retain, insert, insert\_str, as\_mut\_vec, len, is\_empty, split\_off, clear, drain, splice, into\_boxed\_str.
 

### 2022-08-28 article.tex
all swift functions added

@@
 
-    \textbf{C\#}:
+    \textbf{C\#}: Clone, CompareTo, Contains, EndsWith, Equals, GetHashCode, GetType, GetTypeCode, IndexOf, ToLower, ToUpper, Insert, IsNormalized, LastIndexOf, Remove, Replace, Split, StartsWith, Substring, ToCharArray, Trim.
 
-    Clone, CompareTo, Contains, EndsWith, Equals, GetHashCode, GetType, GetTypeCode, IndexOf, ToLower, ToUpper, Insert, IsNormalized, LastIndexOf, Remove, Replace, Split, StartsWith, Substring, ToCharArray, Trim.
-
-    \textbf{Swift}:
+    \textbf{Swift}: init, isZero, isFinite, isInfinite, isEmpty, count, write, append, reserveCapacity, +, +=, +, +, +, +=, insert, replaceSubrange, remove, removeAll, removeFirst, removeLast, significandWidth, removeLast, exponentBitPattern, removeSubrange, significandBitCoun:, removeSubrange, exponentBitCount:, removeSubrange, filter, drop, dropFirst, dropLast, popLast, lowercased, uppercased, ==, !=, <, <=, <=, >, >=, \~=, elementsEqual, starts, lexicographicallyPrecedes, applying, difference, hasPrefix, hasSuffix, contains, allSatisfy, contains.
 

### 2022-08-28 article.tex
all swift functions fixed

--- 2022-08-28 article.tex
@@
 
-    \textbf{C\#}:
+    \textbf{C\#}: Clone, CompareTo, Contains, EndsWith, Equals, GetHashCode, GetType, GetTypeCode, IndexOf, ToLower, ToUpper, Insert, IsNormalized, LastIndexOf, Remove, Replace, Split, StartsWith, Substring, ToCharArray, Trim.
 
-    Clone, CompareTo, Contains, EndsWith, Equals, GetHashCode, GetType, GetTypeCode, IndexOf, ToLower, ToUpper, Insert, IsNormalized, LastIndexOf, Remove, Replace, Split, StartsWith, Substring, ToCharArray, Trim.
-
-    \textbf{Swift}:
+    \textbf{Swift}: init, isZero, isFinite, isInfinite, isEmpty, count, write, append, reserveCapacity, +, +=, insert, replaceSubrange, remove, removeAll, removeFirst, removeLast, significandWidth, removeLast, exponentBitPattern, removeSubrange, significandBitCoun:, removeSubrange, exponentBitCount:, removeSubrange, filter, drop, dropFirst, dropLast, popLast, lowercased, uppercased, ==, !=, <, <=, >, >=, elementsEqual, starts, lexicographicallyPrecedes, applying, difference, hasPrefix, hasSuffix, contains, allSatisfy, contains.
 

### 2022-08-29 article.tex
functions descriptions added in table
amount of functions added

--- 2022-08-28 article.tex
@@
 
-    \textbf{Java}: charAt, codePointAt, codePointBefore, codePointCount, compareTo, compareToIgnoreCase, concat, contains, contentEquals, copyValueOf, endsWith, equals, equalsIgnoreCase, format, getBytes, getChars, hashCode, indexOf, intern, isEmpty, length, lastIndexOf, length, matches, offsetByCodePoints, regionMatches, replace, replaceAll, replaceFirst, split, startsWith, subSequence, substring, toCharArray, toLowerCase, toString, toUpperCase, trim, valueOf.
+    \textbf{Java (39)}: charAt, codePointAt, codePointBefore, codePointCount, compareTo, compareToIgnoreCase, concat, contains, contentEquals, copyValueOf, endsWith, equals, equalsIgnoreCase, format, getBytes, getChars, hashCode, indexOf, intern, isEmpty, length, lastIndexOf, length, matches, offsetByCodePoints, regionMatches, replace, replaceAll, replaceFirst, split, startsWith, subSequence, substring, toCharArray, toLowerCase, toString, toUpperCase, trim, valueOf.
 
-    \textbf{Ruby}: new, try\_convert, \%, *, +, +@, -@, <<, <=>, ==, ===, =\~, [], []=, ascii\_only?, b, bytes, bytesize, byteslice, capitalize, capitalize!, casecmp, casecmp?, center, chars, chomp, chomp!, chop, chop!, chr, clear, codepoints, concat, count, crypt, delete, delete!, delete\_prefix, delete\_prefix!, delete\_suffix, delete\_suffix!, downcase, downcase!, dump, each\_byte, each\_char, each\_codepoint, \\ each\_grapheme\_cluster, each\_line, empty?, encode, encode!, encoding, end\_with?, eql?, force\_encoding, freeze, getbyte, grapheme\_clusters, gsub, gsub!, hash, hex, include?, index, initialize\_copy, insert, inspect, intern, length, lines, ljust, lstrip, lstrip!, match, match?, next, next!, oct, ord, partition, prepend, replace, reverse, reverse!, rindex, rjust, rpartition, rstrip, rstrip!, scan, scrub, scrub!, setbyte, size, slice, slice!, split, squeeze, squeeze!, start\_with?, strip, strip!, sub, sub!, succ, succ!, sum, swapcase, swapcase!, to\_c, to\_f, to\_i, to\_r, to\_s, to\_str, to\_sym, tr, tr!, tr\_s, tr\_s!, undump, unicode\_normalize, unicode\_normalize!, unicode\_normalized?, unpack, unpack1, upcase, upcase!, upto, valid\_encoding?.
+    \textbf{Ruby (132)}: new, try\_convert, \%, *, +, +@, -@, <<, <=>, ==, ===, =\~, [], []=, ascii\_only?, b, bytes, bytesize, byteslice, capitalize, capitalize!, casecmp, casecmp?, center, chars, chomp, chomp!, chop, chop!, chr, clear, codepoints, concat, count, crypt, delete, delete!, delete\_prefix, delete\_prefix!, delete\_suffix, delete\_suffix!, downcase, downcase!, dump, each\_byte, each\_char, each\_codepoint, \\ each\_grapheme\_cluster, each\_line, empty?, encode, encode!, encoding, end\_with?, eql?, force\_encoding, freeze, getbyte, grapheme\_clusters, gsub, gsub!, hash, hex, include?, index, initialize\_copy, insert, inspect, intern, length, lines, ljust, lstrip, lstrip!, match, match?, next, next!, oct, ord, partition, prepend, replace, reverse, reverse!, rindex, rjust, rpartition, rstrip, rstrip!, scan, scrub, scrub!, setbyte, size, slice, slice!, split, squeeze, squeeze!, start\_with?, strip, strip!, sub, sub!, succ, succ!, sum, swapcase, swapcase!, to\_c, to\_f, to\_i, to\_r, to\_s, to\_str, to\_sym, tr, tr!, tr\_s, tr\_s!, undump, unicode\_normalize, unicode\_normalize!, unicode\_normalized?, unpack, unpack1, upcase, upcase!, upto, valid\_encoding?.
 
-    \textbf{Python}: capitalize, casefold, center, count, encode, endswith, expandtabs, find, format, format\_map, index, isalnum, isalpha, isascii, isdecimal, isdigit, isidentifier, islower, isnumeric, isprintable, isspace, istitle, isupper, join, ljust, lower, lstrip, maketrans, partition, replace, rfind, rindex, rjust, rpartition, rsplit, rstrip, split, splitlines, startswith, strip, swapcase, title, translate, upper, zfill.
+    \textbf{Python (45)}: capitalize, casefold, center, count, encode, endswith, expandtabs, find, format, format\_map, index, isalnum, isalpha, isascii, isdecimal, isdigit, isidentifier, islower, isnumeric, isprintable, isspace, istitle, isupper, join, ljust, lower, lstrip, maketrans, partition, replace, rfind, rindex, rjust, rpartition, rsplit, rstrip, split, splitlines, startswith, strip, swapcase, title, translate, upper, zfill.
 
-    \textbf{C++}: append, assign, at, back, begin, c\_str, capacity, cbegin, cend, clear, compare, copy, crbegin, crend, data, empty, end, erase, find, find\_first\_not\_of, find\_first\_of, find\_last\_not\_of, find\_last\_of, front, get\_allocator, insert, length, max\_size, operator[], operator+=, operator=, pop\_back, push\_back, rbegin, rend, replace, reserve, resize, rfind, shrink\_to\_fit, size, substr, swap.
+    \textbf{C++ (43)}: append, assign, at, back, begin, c\_str, capacity, cbegin, cend, clear, compare, copy, crbegin, crend, data, empty, end, erase, find, find\_first\_not\_of, find\_first\_of, find\_last\_not\_of, find\_last\_of, front, get\_allocator, insert, length, max\_size, operator[], operator+=, operator=, pop\_back, push\_back, rbegin, rend, replace, reserve, resize, rfind, shrink\_to\_fit, size, substr, swap.
 
-    \textbf{JavaScript}: charAt, charCodeAt, codePointAt, concat, constructor, endsWith, fromCharCode, includes, indexOf, lastIndexOf, length, localeCompare, match, prototype, repeat, replace, search, slice, split, startsWith, substr, substring, toLocaleLowerCase, toLocaleUpperCase, toLowerCase, toString, toUpperCase, trim, valueOf.
+    \textbf{JavaScript (29)}: charAt, charCodeAt, codePointAt, concat, constructor, endsWith, fromCharCode, includes, indexOf, lastIndexOf, length, localeCompare, match, prototype, repeat, replace, search, slice, split, startsWith, substr, substring, toLocaleLowerCase, toLocaleUpperCase, toLowerCase, toString, toUpperCase, trim, valueOf.
 
-    \textbf{Go}: Clone, Compare, Contains, ContainsAny, ContainsRune, Count, Cut, EqualFold, Fields, FieldsFunc, func, HasPrefix, HasSuffix, Index, IndexAny, IndexByte, IndexFunc, func, IndexRune, Join, LastIndex, LastIndexAny, LastIndexByte, LastIndexFunc, func, Map, func, Repeat, Replace, ReplaceAll, Split, SplitAfter, SplitAfterN, SplitN, Title, ToLower, ToLowerSpecial, ToTitle, ToTitleSpecial, ToUpper, ToUpperSpecial, ToValidUTF8, Trim, TrimFunc, func, TrimLeft, TrimLeftFunc, func, TrimPrefix, TrimRight, TrimRightFunc, func, TrimSpace, TrimSuffix.
+    \textbf{Go (54)}: Clone, Compare, Contains, ContainsAny, ContainsRune, Count, Cut, EqualFold, Fields, FieldsFunc, func, HasPrefix, HasSuffix, Index, IndexAny, IndexByte, IndexFunc, func, IndexRune, Join, LastIndex, LastIndexAny, LastIndexByte, LastIndexFunc, func, Map, func, Repeat, Replace, ReplaceAll, Split, SplitAfter, SplitAfterN, SplitN, Title, ToLower, ToLowerSpecial, ToTitle, ToTitleSpecial, ToUpper, ToUpperSpecial, ToValidUTF8, Trim, TrimFunc, func, TrimLeft, TrimLeftFunc, func, TrimPrefix, TrimRight, TrimRightFunc, func, TrimSpace, TrimSuffix.
 
-    \textbf{C\#}:
+    \textbf{C\# (21)}: Clone, CompareTo, Contains, EndsWith, Equals, GetHashCode, GetType, GetTypeCode, IndexOf, ToLower, ToUpper, Insert, IsNormalized, LastIndexOf, Remove, Replace, Split, StartsWith, Substring, ToCharArray, Trim.
 
-    Clone, CompareTo, Contains, EndsWith, Equals, GetHashCode, GetType, GetTypeCode, IndexOf, ToLower, ToUpper, Insert, IsNormalized, LastIndexOf, Remove, Replace, Split, StartsWith, Substring, ToCharArray, Trim.
+    \textbf{Swift (48)}: init, isZero, isFinite, isInfinite, isEmpty, count, write, append, reserveCapacity, +, +=, insert, replaceSubrange, remove, removeAll, removeFirst, removeLast, significandWidth, removeLast, exponentBitPattern, removeSubrange, significandBitCoun:, removeSubrange, exponentBitCount:, removeSubrange, filter, drop, dropFirst, dropLast, popLast, lowercased, uppercased, ==, !=, <, <=, >, >=, elementsEqual, starts, lexicographicallyPrecedes, applying, difference, hasPrefix, hasSuffix, contains, allSatisfy, contains.
 
-    \textbf{Swift}:
+    \textbf{PHP (98)}: addcslashes, addslashes, bin2hex, chop, chr, chunk\_split, convert\_cyr\_string, convert\_uudecode, convert\_uuencode, count\_chars, crc32, crypt, echo, explode, fprint, get\_html\_translation\_table, hebrev, hebrevc, hex2bin, html\_entity\_decode, htmlentities, htmlspecialchars\_decode, htmlspecialchars, implode, join, lcfirst, levenshtein, localeconv, ltrim, md5, md5\_file, metaphone, money\_format, nl\_langinfo, nl2br, number\_format, ord, parse\_str, print, printf, quoted\_printable\_decode, quoted\_printable\_encode, quotemeta, rtrim, setlocale, sha1, sha1\_file, similar\_text, soundex, sprintf, sscanf, str\_getcsv, str\_ireplace, str\_pad, str\_repeat, str\_replace, str\_rot13, str\_shuffle, str\_split, str\_word\_count, strcasecmp, strchr, strcmp, strcoll, strcspn, strip\_tags, stripcslashes, stripslashes, stripos, stristr, strlen, strnatcasecmp, strnatcmp, strncasecmp, strncmp, strpbrk, strpos, strrchr, strrev, strripos, strrpos, strspn, strstr, strtok, strtolower, strtoupper, strtr, substr, substr\_compare, substr\_count, substr\_replace, trim, ucfirst, ucwords, vfprintf, vprintf, vsprintf, wordwrap.
 
-    \textbf{PHP}: addcslashes, addslashes, bin2hex, chop, chr, chunk\_split, convert\_cyr\_string, convert\_uudecode, convert\_uuencode, count\_chars, crc32, crypt, echo, explode, fprint, get\_html\_translation\_table, hebrev, hebrevc, hex2bin, html\_entity\_decode, htmlentities, htmlspecialchars\_decode, htmlspecialchars, implode, join, lcfirst, levenshtein, localeconv, ltrim, md5, md5\_file, metaphone, money\_format, nl\_langinfo, nl2br, number\_format, ord, parse\_str, print, printf, quoted\_printable\_decode, quoted\_printable\_encode, quotemeta, rtrim, setlocale, sha1, sha1\_file, similar\_text, soundex, sprintf, sscanf, str\_getcsv, str\_ireplace, str\_pad, str\_repeat, str\_replace, str\_rot13, str\_shuffle, str\_split, str\_word\_count, strcasecmp, strchr, strcmp, strcoll, strcspn, strip\_tags, stripcslashes, stripslashes, stripos, stristr, strlen, strnatcasecmp, strnatcmp, strncasecmp, strncmp, strpbrk, strpos, strrchr, strrev, strripos, strrpos, strspn, strstr, strtok, strtolower, strtoupper, strtr, substr, substr\_compare, substr\_count, substr\_replace, trim, ucfirst, ucwords, vfprintf, vprintf, vsprintf, wordwrap.
-
-    \textbf{Rust}: new, with\_capacity, from\_utf8, from\_utf8\_lossy, from\_utf16, from\_utf16\_lossy, from\_raw\_parts, from\_utf8\_unchecked, into\_bytes, as\_str, as\_mut\_str, push\_str, capacity, reserve, reserve\_exact, try\_reserve, try\_reserve\_exact, shrink\_to\_fit, shrink\_to, push, as\_bytes, truncate, pop, remove, retain, insert, insert\_str, as\_mut\_vec, len, is\_empty, split\_off, clear, drain, splice, into\_boxed\_str.
+    \textbf{Rust (35)}: new, with\_capacity, from\_utf8, from\_utf8\_lossy, from\_utf16, from\_utf16\_lossy, from\_raw\_parts, from\_utf8\_unchecked, into\_bytes, as\_str, as\_mut\_str, push\_str, capacity, reserve, reserve\_exact, try\_reserve, try\_reserve\_exact, shrink\_to\_fit, shrink\_to, push, as\_bytes, truncate, pop, remove, retain, insert, insert\_str, as\_mut\_vec, len, is\_empty, split\_off, clear, drain, splice, into\_boxed\_str.
 
@@
 
-            capitalize &  &  &  &  &  & &  &  & 1 & 1 \\
+            String \textbf{capitalize} &  &  &  &  &  & &  &  & 1 & 1 \\
 
@@
 
-            compare &  &  &  &  &  & &  &  & n & n \\
+            Strings \textbf{compare} &  &  &  &  &  & &  &  & n & n \\
 
-            compare-ignore-case &  &  &  &  &  & &  &  &  & \\
+            Strings \textbf{compare-ignore-case} &  &  &  &  &  & &  &  &  & \\
 
-            concatenate &  &  &  &  &  & &  &  & n & n \\
+            Strings \textbf{concatenate} &  &  &  &  &  & &  &  & n & n \\
 
-            containts &  &  &  &  &  & &  &  & n & n \\
+            Check if \textbf{containts} substring &  &  &  &  &  & &  &  & n & n \\
 
-            count &  &  &  &  &  & &  &  &  & \\
+            \textbf{count} of substring in string &  &  &  &  &  & &  &  &  & \\
 
-            ends-with &  &  &  &  &  & &  &  & n & n \\
+            Check if \textbf{ends-with} a substring &  &  &  &  &  & &  &  & n & n \\
 
-            equals &  &  &  &  &  & &  &  & n & n \\
+            Check if \textbf{equals} &  &  &  &  &  & &  &  & n & n \\
 
-            find-first &  &  &  &  &  & &  &  & n & n \\
+            \textbf{find-first} substring in string &  &  &  &  &  & &  &  & n & n \\
 
-            find-last &  &  &  &  &  & &  &  & n & n \\
+            \textbf{find-last} substring in string &  &  &  &  &  & &  &  & n & n \\
 
-            format &  &  &  &  &  & &  &  & n & n \\
+            \textbf{format} string by regexp &  &  &  &  &  & &  &  & n & n \\
 
-            hash &  &  &  &  &  & &  &  & n & n \\
+            Get string \textbf{hash} &  &  &  &  &  & &  &  & n & n \\
 
-            insert &  &  &  &  &  & &  &  & n & n \\
+            \textbf{insert} in string by index &  &  &  &  &  & &  &  & n & n \\
 
-            is-alphabetic &  &  &  &  &  & &  &  & n & n \\
+            Check if \textbf{is-alphabetic} &  &  &  &  &  & &  &  & n & n \\
 
-            is-empty &  &  &  &  &  & &  &  & 1 & 1 \\
+            Check if \textbf{is-empty} &  &  &  &  &  & &  &  & 1 & 1 \\
 
-            is-hexadecimal &  &  &  &  &  & &  &  & n & n \\
+            Check if \textbf{is-hexadecimal} &  &  &  &  &  & &  &  & n & n \\
 
-            is-int &  &  &  &  &  & &  &  & n & n \\
+            Check if \textbf{is-int} &  &  &  &  &  & &  &  & n & n \\
 
-            is-lowercase &  &  &  &  &  & &  &  & n & n \\
+            Check if \textbf{is-lowercase} &  &  &  &  &  & &  &  & n & n \\
 
-            is-uppercase &  &  &  &  &  & &  &  & n & n \\
+            Check if \textbf{is-uppercase} &  &  &  &  &  & &  &  & n & n \\
 
-            is-whitespace &  &  &  &  &  & &  &  & n & n \\
+            Check if \textbf{is-whitespace} &  &  &  &  &  & &  &  & n & n \\
 
-            join &  &  &  &  &  & &  &  & n & n \\
+            \textbf{join} list of strings &  &  &  &  &  & &  &  & n & n \\
 
-            length &  &  &  &  &  & &  &  & 1 & 1 \\
+            Get string \textbf{length} &  &  &  &  &  & &  &  & 1 & 1 \\
 
-            matches-regexp &  &  &  &  &  & &  &  & n & n \\
+            Check if string \textbf{matches-regexp} &  &  &  &  &  & &  &  & n & n \\
 
-            partition &  &  &  &  &  & &  &  & n & n \\
+            Get string \textbf{partition} &  &  &  &  &  & &  &  & n & n \\
 
-            repeat &  &  &  &  &  & &  &  & n & n \\
+            \textbf{repeat} string number of times &  &  &  &  &  & &  &  & n & n \\
 
-            replace-all &  &  &  &  &  & &  &  & n & n \\
+            \textbf{replace-all} substrings by other &  &  &  &  &  & &  &  & n & n \\
 
-            replace-first &  &  &  &  &  &  &  &  &  & \\
+            \textbf{replace-first} substrings by other &  &  &  &  &  &  &  &  &  & \\
 
-            split &  &  &  &  &  & &  &  & n & n \\
+            String \textbf{split} &  &  &  &  &  & &  &  & n & n \\
 
-            starts-with &  &  &  &  &  & &  &  & n & n \\
+            Check if \textbf{starts-with} a substring &  &  &  &  &  & &  &  & n & n \\
 
-            strip &  &  &  &  &  & &  &  & n & n \\
+            String \textbf{strip} &  &  &  &  &  & &  &  & n & n \\
 
-            substring &  &  &  &  &  & &  &  & n & 1 \\
+            Get \textbf{substring} by positions &  &  &  &  &  & &  &  & n & 1 \\
 
-            swap-case &  &  &  &  &  & &  &  & n & n \\
+            String \textbf{swap-case} &  &  &  &  &  & &  &  & n & n \\
 
-            to-float &  &  &  &  &  & &  &  & n & n \\
+            String \textbf{to-float} &  &  &  &  &  & &  &  & n & n \\
 
-            to-int &  &  &  &  &  & &  &  & n & n \\
+            String \textbf{to-int} &  &  &  &  &  & &  &  & n & n \\
 
-            to-lowercase &  &  &  &  &  & &  &  & n & n \\
+            String \textbf{to-lowercase} &  &  &  &  &  & &  &  & n & n \\
 
-            to-uppercase &  &  &  &  &  & &  &  & n & n \\
+            String \textbf{to-uppercase} &  &  &  &  &  & &  &  & n & n \\
 
-            trim-left &  &  &  &  &  & &  &  & n & n \\
+            String \textbf{trim-left} &  &  &  &  &  &  &  &  & n & n \\
 
-            trim-right &  &  &  &  &  & &  &  & n & n \\
+            String \textbf{trim-righ} &  &  &  &  &  & &  &  & n & n \\
 
-            reverse &  &  &  &  &  & &  &  & n & 1 \\
+            String \textbf{reverse} &  &  &  &  &  & &  &  & n & 1 \\
 
-            remove &  &  &  &  &  & &  &  &  & \\
+            \textbf{remove} substring by positions &  &  &  &  &  & &  &  &  & \\
 
-            uncapitalize &  &  &  &  &  & &  &  &  & \\
+            String \textbf{uncapitalize} &  &  &  &  &  & &  &  &  & \\
 
-            as-bytes &  &  &  &  &  & &  &  &  & \\
+            Get string \textbf{as-bytes} &  &  &  &  &  & &  &  &  & \\
 
-            chop &  &  &  &  &  & &  &  &  & \\ \hline
+            String \textbf{cut-end} &  &  &  &  &  & &  &  &  & \\ \hline
+
         \end{tabular}

### 2022-08-29 article.tex
more methods added

@@
 
-    \textbf{Swift (48)}: init, isZero, isFinite, isInfinite, isEmpty, count, write, append, reserveCapacity, +, +=, insert, replaceSubrange, remove, removeAll, removeFirst, removeLast, significandWidth, removeLast, exponentBitPattern, removeSubrange, significandBitCoun:, removeSubrange, exponentBitCount:, removeSubrange, filter, drop, dropFirst, dropLast, popLast, lowercased, uppercased, ==, !=, <, <=, >, >=, elementsEqual, starts, lexicographicallyPrecedes, applying, difference, hasPrefix, hasSuffix, contains, allSatisfy, contains.
+    \textbf{Swift (48)}: init, isZero, isFinite, isInfinite, isEmpty, count, write, append, reserveCapacity, +, +=, insert, replaceSubrange, remove, removeAll, removeFirst, removeLast, significandWidth, removeLast, exponentBitPattern, removeSubrange, significandBitCoun, removeSubrange, exponentBitCount, removeSubrange, filter, drop, dropFirst, dropLast, popLast, lowercased, uppercased, ==, !=, <, <=, >, >=, elementsEqual, starts, lexicographicallyPrecedes, applying, difference, hasPrefix, hasSuffix, contains, allSatisfy, contains.
 
@@
 
-            String \textbf{cut-end} &  &  &  &  &  & &  &  &  & \\ \hline
+            String \textbf{pop-back} &  &  &  &  &  & &  &  &  & \\
+
+            Get string \textbf{as-chars} &  &  &  &  &  & &  &  &  & \\
+
+            Get string \textbf{as-canonical} &  &  &  &  &  & &  &  &  & \\
+
+            Check if \textbf{is-ascii}  &  &  &  &  &  & &  &  &  & \\
+
+            String \textbf{copy} &  &  &  &  &  & &  &  &  & \\
+
+            String \textbf{contains-any} &  &  &  &  &  & &  &  &  & \\
+
+            String \textbf{reserve-capacity} &  &  &  &  &  & &  &  &  & \\
+
+            String \textbf{shrink-to-fit} &  &  &  &  &  & &  &  &  & \\ \hline
 

### 2022-08-29 article.tex
longtable using
java functions existing added

@@
 
+\usepackage{longtable}
 \usepackage{rotating}
@@
 
-    \begin{table*}
-        \begin{tabular}{lllllllllll}
+    \begin{longtable}{lllllllllll}
         \hline
@@
         & \begin{sideways}Rust\end{sideways}
-            \\ \hline
+        \\
+        \hline
+        \endfirsthead
+        \multicolumn{11}{c}%
+        {\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
+        \hline
+        & \begin{sideways}Java\end{sideways}
+        & \begin{sideways}Ruby\end{sideways}
+        & \begin{sideways}Python\end{sideways}
+        & \begin{sideways}C++\end{sideways}
+        & \begin{sideways}JavaScript\end{sideways}
+        & \begin{sideways}Go\end{sideways}
+        & \begin{sideways}C\#\end{sideways}
+        & \begin{sideways}Swift\end{sideways}
+        & \begin{sideways}PHP\end{sideways}
+        & \begin{sideways}Rust\end{sideways}
+        \\
+        \hline
+        \endhead
+        \hline \multicolumn{11}{r}{\textit{Continued on next page}} \\
+        \endfoot
+        \hline
+        \endlastfoot
+        String \textbf{capitalize} & No &  &  &  &  & &  &  & 1 & 1 \\
 
-            String \textbf{capitalize} &  &  &  &  &  & &  &  & 1 & 1 \\
+        Get \textbf{char-at} a given position & Yes &  &  &  &  & &  &  & 1 & 1 \\
 
-            Get \textbf{char-at} a given position &  &  &  &  &  & &  &  & 1 & 1 \\
+        Strings \textbf{compare} & Yes &  &  &  &  & &  &  & n & n \\
 
-            Strings \textbf{compare} &  &  &  &  &  & &  &  & n & n \\
+        Strings \textbf{compare-ignore-case} & Yes &  &  &  &  & &  &  &  & \\
 
-            Strings \textbf{compare-ignore-case} &  &  &  &  &  & &  &  &  & \\
+        Strings \textbf{concatenate} & Yes &  &  &  &  & &  &  & n & n \\
 
-            Strings \textbf{concatenate} &  &  &  &  &  & &  &  & n & n \\
+        Check if \textbf{containts} substring & Yes &  &  &  &  & &  &  & n & n \\
 
-            Check if \textbf{containts} substring &  &  &  &  &  & &  &  & n & n \\
+        \textbf{count} of substring in string & No &  &  &  &  & &  &  &  & \\
 
-            \textbf{count} of substring in string &  &  &  &  &  & &  &  &  & \\
+        Check if \textbf{ends-with} a substring & Yes &  &  &  &  & &  &  & n & n \\
 
-            Check if \textbf{ends-with} a substring &  &  &  &  &  & &  &  & n & n \\
+        Check if \textbf{equals} & Yes &  &  &  &  & &  &  & n & n \\
 
-            Check if \textbf{equals} &  &  &  &  &  & &  &  & n & n \\
+        \textbf{find-first} substring in string & Yes &  &  &  &  & &  &  & n & n \\
 
-            \textbf{find-first} substring in string &  &  &  &  &  & &  &  & n & n \\
+        \textbf{find-last} substring in string & Yes &  &  &  &  & &  &  & n & n \\
 
-            \textbf{find-last} substring in string &  &  &  &  &  & &  &  & n & n \\
+        \textbf{format} string by regexp & Yes &  &  &  &  & &  &  & n & n \\
 
-            \textbf{format} string by regexp &  &  &  &  &  & &  &  & n & n \\
+        Get string \textbf{hash} & Yes &  &  &  &  & &  &  & n & n \\
 
-            Get string \textbf{hash} &  &  &  &  &  & &  &  & n & n \\
+        \textbf{insert} in string by index & No &  &  &  &  & &  &  & n & n \\
 
-            \textbf{insert} in string by index &  &  &  &  &  & &  &  & n & n \\
+        Check if \textbf{is-alphabetic} & No &  &  &  &  & &  &  & n & n \\
 
-            Check if \textbf{is-alphabetic} &  &  &  &  &  & &  &  & n & n \\
+        Check if \textbf{is-empty} & Yes &  &  &  &  & &  &  & 1 & 1 \\
 
-            Check if \textbf{is-empty} &  &  &  &  &  & &  &  & 1 & 1 \\
+        Check if \textbf{is-hexadecimal} & No &  &  &  &  & &  &  & n & n \\
 
-            Check if \textbf{is-hexadecimal} &  &  &  &  &  & &  &  & n & n \\
+        Check if \textbf{is-int} & No &  &  &  &  & &  &  & n & n \\
 
-            Check if \textbf{is-int} &  &  &  &  &  & &  &  & n & n \\
+        Check if \textbf{is-lowercase} & No &  &  &  &  & &  &  & n & n \\
 
-            Check if \textbf{is-lowercase} &  &  &  &  &  & &  &  & n & n \\
+        Check if \textbf{is-uppercase} & No &  &  &  &  & &  &  & n & n \\
 
-            Check if \textbf{is-uppercase} &  &  &  &  &  & &  &  & n & n \\
+        Check if \textbf{is-whitespace} & No &  &  &  &  & &  &  & n & n \\
 
-            Check if \textbf{is-whitespace} &  &  &  &  &  & &  &  & n & n \\
+        \textbf{join} list of strings & No &  &  &  &  & &  &  & n & n \\
 
-            \textbf{join} list of strings &  &  &  &  &  & &  &  & n & n \\
+        Get string \textbf{length} & Yes &  &  &  &  & &  &  & 1 & 1 \\
 
-            Get string \textbf{length} &  &  &  &  &  & &  &  & 1 & 1 \\
+        Check if string \textbf{matches-regexp} & Yes &  &  &  &  & &  &  & n & n \\
 
-            Check if string \textbf{matches-regexp} &  &  &  &  &  & &  &  & n & n \\
+        Get string \textbf{partition} & No &  &  &  &  & &  &  & n & n \\
 
-            Get string \textbf{partition} &  &  &  &  &  & &  &  & n & n \\
+        \textbf{repeat} string number of times & No &  &  &  &  & &  &  & n & n \\
 
-            \textbf{repeat} string number of times &  &  &  &  &  & &  &  & n & n \\
+        \textbf{replace-all} substrings by other & Yes &  &  &  &  & &  &  & n & n \\
 
-            \textbf{replace-all} substrings by other &  &  &  &  &  & &  &  & n & n \\
+        \textbf{replace-first} substrings by other & Yes &  &  &  &  &  &  &  &  & \\
 
-            \textbf{replace-first} substrings by other &  &  &  &  &  &  &  &  &  & \\
+        String \textbf{split} & Yes &  &  &  &  & &  &  & n & n \\
 
-            String \textbf{split} &  &  &  &  &  & &  &  & n & n \\
+        Check if \textbf{starts-with} a substring & Yes &  &  &  &  & &  &  & n & n \\
 
-            Check if \textbf{starts-with} a substring &  &  &  &  &  & &  &  & n & n \\
+        String \textbf{strip} & Yes &  &  &  &  & &  &  & n & n \\
 
-            String \textbf{strip} &  &  &  &  &  & &  &  & n & n \\
+        Get \textbf{substring} by positions & Yes &  &  &  &  & &  &  & n & 1 \\
 
-            Get \textbf{substring} by positions &  &  &  &  &  & &  &  & n & 1 \\
+        String \textbf{swap-case} & No &  &  &  &  & &  &  & n & n \\
 
-            String \textbf{swap-case} &  &  &  &  &  & &  &  & n & n \\
+        String \textbf{to-float} & No &  &  &  &  & &  &  & n & n \\
 
-            String \textbf{to-float} &  &  &  &  &  & &  &  & n & n \\
+        String \textbf{to-int} & No &  &  &  &  & &  &  & n & n \\
 
-            String \textbf{to-int} &  &  &  &  &  & &  &  & n & n \\
+        String \textbf{to-lowercase} & Yes &  &  &  &  & &  &  & n & n \\
 
-            String \textbf{to-lowercase} &  &  &  &  &  & &  &  & n & n \\
+        String \textbf{to-uppercase} & Yes &  &  &  &  & &  &  & n & n \\
 
-            String \textbf{to-uppercase} &  &  &  &  &  & &  &  & n & n \\
+        String \textbf{trim-left} & No &  &  &  &  &  &  &  & n & n \\
 
-            String \textbf{trim-left} &  &  &  &  &  &  &  &  & n & n \\
+        String \textbf{trim-right} & No &  &  &  &  & &  &  & n & n \\
 
-            String \textbf{trim-righ} &  &  &  &  &  & &  &  & n & n \\
+        \textbf{remove} substring by positions & No &  &  &  &  & &  &  &  & \\
 
-            String \textbf{reverse} &  &  &  &  &  & &  &  & n & 1 \\
+        String \textbf{uncapitalize} & No &  &  &  &  & &  &  &  & \\
 
-            \textbf{remove} substring by positions &  &  &  &  &  & &  &  &  & \\
+        Get string \textbf{as-bytes} & Yes &  &  &  &  & &  &  &  & \\
 
-            String \textbf{uncapitalize} &  &  &  &  &  & &  &  &  & \\
+        String \textbf{pop-back} & No &  &  &  &  & &  &  &  & \\
 
-            Get string \textbf{as-bytes} &  &  &  &  &  & &  &  &  & \\
+        Get string \textbf{as-chars} & Yes &  &  &  &  & &  &  &  & \\
 
-            String \textbf{pop-back} &  &  &  &  &  & &  &  &  & \\
+        Get string \textbf{as-canonical} & Yes &  &  &  &  & &  &  &  & \\
 
-            Get string \textbf{as-chars} &  &  &  &  &  & &  &  &  & \\
+        Check if \textbf{is-ascii} & No &  &  &  &  & &  &  &  & \\
 
-            Get string \textbf{as-canonical} &  &  &  &  &  & &  &  &  & \\
+        String \textbf{copy} & Yes &  &  &  &  & &  &  &  & \\
 
-            Check if \textbf{is-ascii}  &  &  &  &  &  & &  &  &  & \\
+        String \textbf{contains-any} & No &  &  &  &  & &  &  &  & \\
 
-            String \textbf{copy} &  &  &  &  &  & &  &  &  & \\
+        String \textbf{reserve-capacity} & No &  &  &  &  & &  &  &  & \\
 
-            String \textbf{contains-any} &  &  &  &  &  & &  &  &  & \\
-
-            String \textbf{reserve-capacity} &  &  &  &  &  & &  &  &  & \\
-
-            String \textbf{shrink-to-fit} &  &  &  &  &  & &  &  &  & \\ \hline
-
-        \end{tabular}
+        String \textbf{shrink-to-fit} & No &  &  &  &  & &  &  &  & \\ \hline
         \caption{String functions existing in languages}
         \label{tab:my_label}
-    \end{table*}
+    \end{longtable}
 

### 2022-08-29 article.tex
python functions existing added

@@
         \endlastfoot
-        String \textbf{capitalize} & No &  &  &  &  & &  &  & 1 & 1 \\
+        String \textbf{capitalize} & No & Yes &  &  &  & &  &  & 1 & 1 \\
 
-        Get \textbf{char-at} a given position & Yes &  &  &  &  & &  &  & 1 & 1 \\
+        Get \textbf{char-at} a given position & Yes & Yes &  &  &  & &  &  & 1 & 1 \\
 
-        Strings \textbf{compare} & Yes &  &  &  &  & &  &  & n & n \\
+        Strings \textbf{compare} & Yes & No &  &  &  & &  &  & n & n \\
 
@@
 
-        Strings \textbf{concatenate} & Yes &  &  &  &  & &  &  & n & n \\
+        Strings \textbf{concatenate} & Yes & No &  &  &  & &  &  & n & n \\
 
-        Check if \textbf{containts} substring & Yes &  &  &  &  & &  &  & n & n \\
+        Check if \textbf{contains} substring & Yes & No &  &  &  & &  &  & n & n \\
 
-        \textbf{count} of substring in string & No &  &  &  &  & &  &  &  & \\
+        \textbf{count} of substring in string & No & Yes &  &  &  & &  &  &  & \\
 
-        Check if \textbf{ends-with} a substring & Yes &  &  &  &  & &  &  & n & n \\
+        Check if \textbf{ends-with} a substring & Yes & Yes &  &  &  & &  &  & n & n \\
 
-        Check if \textbf{equals} & Yes &  &  &  &  & &  &  & n & n \\
+        Check if \textbf{equals} & Yes & No &  &  &  & &  &  & n & n \\
 
-        \textbf{find-first} substring in string & Yes &  &  &  &  & &  &  & n & n \\
+        \textbf{find-first} substring in string & Yes & Yes &  &  &  & &  &  & n & n \\
 
-        \textbf{find-last} substring in string & Yes &  &  &  &  & &  &  & n & n \\
+        \textbf{find-last} substring in string & Yes & No &  &  &  & &  &  & n & n \\
 
-        \textbf{format} string by regexp & Yes &  &  &  &  & &  &  & n & n \\
+        \textbf{format} string by regexp & Yes & Yes &  &  &  & &  &  & n & n \\
 
-        Get string \textbf{hash} & Yes &  &  &  &  & &  &  & n & n \\
+        Get string \textbf{hash} & Yes & No &  &  &  & &  &  & n & n \\
 
-        \textbf{insert} in string by index & No &  &  &  &  & &  &  & n & n \\
+        \textbf{insert} in string by index & No & No &  &  &  & &  &  & n & n \\
 
-        Check if \textbf{is-alphabetic} & No &  &  &  &  & &  &  & n & n \\
+        Check if \textbf{is-alphabetic} & No & Yes &  &  &  & &  &  & n & n \\
 
-        Check if \textbf{is-empty} & Yes &  &  &  &  & &  &  & 1 & 1 \\
+        Check if \textbf{is-empty} & Yes & Yes &  &  &  & &  &  & 1 & 1 \\
 
-        Check if \textbf{is-hexadecimal} & No &  &  &  &  & &  &  & n & n \\
+        Check if \textbf{is-hexadecimal} & No & No &  &  &  & &  &  & n & n \\
 
-        Check if \textbf{is-int} & No &  &  &  &  & &  &  & n & n \\
+        Check if \textbf{is-int} & No & Yes &  &  &  & &  &  & n & n \\
 
-        Check if \textbf{is-lowercase} & No &  &  &  &  & &  &  & n & n \\
+        Check if \textbf{is-lowercase} & No & Yes &  &  &  & &  &  & n & n \\
 
-        Check if \textbf{is-uppercase} & No &  &  &  &  & &  &  & n & n \\
+        Check if \textbf{is-uppercase} & No & Yes &  &  &  & &  &  & n & n \\
 
-        Check if \textbf{is-whitespace} & No &  &  &  &  & &  &  & n & n \\
+        Check if \textbf{is-whitespace} & No & Yes &  &  &  & &  &  & n & n \\
 
-        \textbf{join} list of strings & No &  &  &  &  & &  &  & n & n \\
+        \textbf{join} list of strings & No & Yes &  &  &  & &  &  & n & n \\
 
-        Get string \textbf{length} & Yes &  &  &  &  & &  &  & 1 & 1 \\
+        Get string \textbf{length} & Yes & No &  &  &  & &  &  & 1 & 1 \\
 
-        Check if string \textbf{matches-regexp} & Yes &  &  &  &  & &  &  & n & n \\
+        Check if string \textbf{matches-regexp} & Yes & No &  &  &  & &  &  & n & n \\
 
-        Get string \textbf{partition} & No &  &  &  &  & &  &  & n & n \\
+        Get string \textbf{partition} & No & Yes &  &  &  & &  &  & n & n \\
 
-        \textbf{repeat} string number of times & No &  &  &  &  & &  &  & n & n \\
+        \textbf{repeat} string number of times & No & No &  &  &  & &  &  & n & n \\
 
-        \textbf{replace-all} substrings by other & Yes &  &  &  &  & &  &  & n & n \\
+        \textbf{replace-all} substrings by other & Yes & Yes &  &  &  & &  &  & n & n \\
 
-        \textbf{replace-first} substrings by other & Yes &  &  &  &  &  &  &  &  & \\
+        \textbf{replace-first} substrings by other & Yes & Yes &  &  &  &  &  &  &  & \\
 
-        String \textbf{split} & Yes &  &  &  &  & &  &  & n & n \\
+        String \textbf{split} & Yes & Yes &  &  &  & &  &  & n & n \\
 
-        Check if \textbf{starts-with} a substring & Yes &  &  &  &  & &  &  & n & n \\
+        Check if \textbf{starts-with} a substring & Yes & Yes &  &  &  & &  &  & n & n \\
 
-        String \textbf{strip} & Yes &  &  &  &  & &  &  & n & n \\
+        String \textbf{strip} & Yes & Yes &  &  &  & &  &  & n & n \\
 
-        Get \textbf{substring} by positions & Yes &  &  &  &  & &  &  & n & 1 \\
+        Get \textbf{substring} by positions & Yes & No &  &  &  & &  &  & n & 1 \\
 
-        String \textbf{swap-case} & No &  &  &  &  & &  &  & n & n \\
+        String \textbf{swap-case} & No & Yes &  &  &  & &  &  & n & n \\
 
-        String \textbf{to-float} & No &  &  &  &  & &  &  & n & n \\
+        String \textbf{to-float} & No & No &  &  &  & &  &  & n & n \\
 
-        String \textbf{to-int} & No &  &  &  &  & &  &  & n & n \\
+        String \textbf{to-int} & No & No &  &  &  & &  &  & n & n \\
 
-        String \textbf{to-lowercase} & Yes &  &  &  &  & &  &  & n & n \\
+        String \textbf{to-lowercase} & Yes & Yes &  &  &  & &  &  & n & n \\
 
-        String \textbf{to-uppercase} & Yes &  &  &  &  & &  &  & n & n \\
+        String \textbf{to-uppercase} & Yes & Yes &  &  &  & &  &  & n & n \\
 
-        String \textbf{trim-left} & No &  &  &  &  &  &  &  & n & n \\
+        String \textbf{trim-left} & No & Yes &  &  &  &  &  &  & n & n \\
 
-        String \textbf{trim-right} & No &  &  &  &  & &  &  & n & n \\
+        String \textbf{trim-right} & No & Yes &  &  &  & &  &  & n & n \\
 
-        \textbf{remove} substring by positions & No &  &  &  &  & &  &  &  & \\
+        \textbf{remove} substring by positions & No & No &  &  &  & &  &  &  & \\
 
-        String \textbf{uncapitalize} & No &  &  &  &  & &  &  &  & \\
+        String \textbf{uncapitalize} & No & No &  &  &  & &  &  &  & \\
 
-        Get string \textbf{as-bytes} & Yes &  &  &  &  & &  &  &  & \\
+        Get string \textbf{as-bytes} & Yes & No &  &  &  & &  &  &  & \\
 
-        String \textbf{pop-back} & No &  &  &  &  & &  &  &  & \\
+        String \textbf{pop-back} & No & No &  &  &  & &  &  &  & \\
 
-        Get string \textbf{as-chars} & Yes &  &  &  &  & &  &  &  & \\
+        Get string \textbf{as-chars} & Yes & No &  &  &  & &  &  &  & \\
 
-        Get string \textbf{as-canonical} & Yes &  &  &  &  & &  &  &  & \\
+        Get string \textbf{as-canonical} & Yes & No &  &  &  & &  &  &  & \\
 
-        Check if \textbf{is-ascii} & No &  &  &  &  & &  &  &  & \\
+        Check if \textbf{is-ascii} & No & Yes &  &  &  & &  &  &  & \\
 
-        String \textbf{copy} & Yes &  &  &  &  & &  &  &  & \\
+        String \textbf{copy} & Yes & No &  &  &  & &  &  &  & \\
 
-        String \textbf{contains-any} & No &  &  &  &  & &  &  &  & \\
+        String \textbf{contains-any} & No & No &  &  &  & &  &  &  & \\
 
-        String \textbf{reserve-capacity} & No &  &  &  &  & &  &  &  & \\
+        String \textbf{reserve-capacity} & No & No &  &  &  & &  &  &  & \\
 
-        String \textbf{shrink-to-fit} & No &  &  &  &  & &  &  &  & \\ \hline
+        String \textbf{shrink-to-fit} & No & No &  &  &  & &  &  &  & \\ \hline
         \caption{String functions existing in languages}

### 2022-08-30 article.tex
existing table filled

--- 2022-08-29 article.tex
@@
 
+\usepackage{amssymb}
 \usepackage{rotating}
@@
 
-    \hl{todo}
+    \hl{todo add link to parsing repo}
 
@@
 
-    \textbf{Rust (35)}: new, with\_capacity, from\_utf8, from\_utf8\_lossy, from\_utf16, from\_utf16\_lossy, from\_raw\_parts, from\_utf8\_unchecked, into\_bytes, as\_str, as\_mut\_str, push\_str, capacity, reserve, reserve\_exact, try\_reserve, try\_reserve\_exact, shrink\_to\_fit, shrink\_to, push, as\_bytes, truncate, pop, remove, retain, insert, insert\_str, as\_mut\_vec, len, is\_empty, split\_off, clear, drain, splice, into\_boxed\_str.
+    \textbf{Rust (105)}: new, with\_capacity, from\_utf8, from\_utf8\_lossy, from\_utf16, from\_utf16\_lossy, from\_raw\_parts, from\_utf8\_unchecked, into\_bytes, as\_str, as\_mut\_str, push\_str, capacity, reserve, reserve\_exact, try\_reserve, try\_reserve\_exact, shrink\_to\_fit, shrink\_to, push, as\_bytes, truncate, pop, remove, retain, insert, insert\_str, as\_mut\_vec, len, is\_empty, split\_off, clear, drain, splice, into\_boxed\_str, as\_bytes, as\_bytes\_mut, as\_mut\_ptr, as\_ptr, bytes, ceil\_char\_boundary, char\_indices, chars, contains, encode\_utf16, ends\_with, eq\_ignore\_ascii\_case, escape\_debug, escape\_default, escape\_unicode, find, floor\_char\_boundary, get, get\_mut, get\_unchecked, get\_unchecked\_mut, is\_ascii, is\_char\_boundary, is\_empty, len, lines, lines\_any, make\_ascii\_lowercase, make\_ascii\_uppercase, match\_indices, matches, parse, repeat, replace, replacen, rfind, rmatch\_indices, rmatches, rsplit, rsplit\_once, rsplit\_terminator, rsplitn, slice\_mut\_unchecked, slice\_unchecked, split, split\_ascii\_whitespace, split\_at, split\_at\_mut, split\_inclusive, split\_once, split\_terminator, split\_whitespace, splitn, starts\_with, strip\_prefix, strip\_suffix, to\_ascii\_lowercase, to\_ascii\_uppercase, to\_lowercase, to\_uppercase, trim, trim\_end, trim\_end\_matches, trim\_left, trim\_left\_matches, trim\_matches, trim\_right, trim\_right\_matches, trim\_start, trim\_start\_matches.
 
@@
             \\ \hline
-
-            String \textbf{capitalize} &  &  &  &  &  & &  &  & 1 & 1 \\
-
-            Get \textbf{char-at} a given position &  &  &  &  &  & &  &  & 1 & 1 \\
-
-            Strings \textbf{compare} &  &  &  &  &  & &  &  & n & n \\
-
-            Strings \textbf{compare-ignore-case} &  &  &  &  &  & &  &  &  & \\
-
-            Strings \textbf{concatenate} &  &  &  &  &  & &  &  & n & n \\
-
-            Check if \textbf{containts} substring &  &  &  &  &  & &  &  & n & n \\
-
-            \textbf{count} of substring in string &  &  &  &  &  & &  &  &  & \\
-
-            Check if \textbf{ends-with} a substring &  &  &  &  &  & &  &  & n & n \\
-
-            Check if \textbf{equals} &  &  &  &  &  & &  &  & n & n \\
-
-            \textbf{find-first} substring in string &  &  &  &  &  & &  &  & n & n \\
-
-            \textbf{find-last} substring in string &  &  &  &  &  & &  &  & n & n \\
-
-            \textbf{format} string by regexp &  &  &  &  &  & &  &  & n & n \\
-
-            Get string \textbf{hash} &  &  &  &  &  & &  &  & n & n \\
-
-            \textbf{insert} in string by index &  &  &  &  &  & &  &  & n & n \\
-
-            Check if \textbf{is-alphabetic} &  &  &  &  &  & &  &  & n & n \\
-
-            Check if \textbf{is-empty} &  &  &  &  &  & &  &  & 1 & 1 \\
-
-            Check if \textbf{is-hexadecimal} &  &  &  &  &  & &  &  & n & n \\
-
-            Check if \textbf{is-int} &  &  &  &  &  & &  &  & n & n \\
-
-            Check if \textbf{is-lowercase} &  &  &  &  &  & &  &  & n & n \\
-
-            Check if \textbf{is-uppercase} &  &  &  &  &  & &  &  & n & n \\
-
-            Check if \textbf{is-whitespace} &  &  &  &  &  & &  &  & n & n \\
-
-            \textbf{join} list of strings &  &  &  &  &  & &  &  & n & n \\
-
-            Get string \textbf{length} &  &  &  &  &  & &  &  & 1 & 1 \\
-
-            Check if string \textbf{matches-regexp} &  &  &  &  &  & &  &  & n & n \\
-
-            Get string \textbf{partition} &  &  &  &  &  & &  &  & n & n \\
-
-            \textbf{repeat} string number of times &  &  &  &  &  & &  &  & n & n \\
-
-            \textbf{replace-all} substrings by other &  &  &  &  &  & &  &  & n & n \\
-
-            \textbf{replace-first} substrings by other &  &  &  &  &  &  &  &  &  & \\
-
-            String \textbf{split} &  &  &  &  &  & &  &  & n & n \\
-
-            Check if \textbf{starts-with} a substring &  &  &  &  &  & &  &  & n & n \\
-
-            String \textbf{strip} &  &  &  &  &  & &  &  & n & n \\
-
-            Get \textbf{substring} by positions &  &  &  &  &  & &  &  & n & 1 \\
-
-            String \textbf{swap-case} &  &  &  &  &  & &  &  & n & n \\
-
-            String \textbf{to-float} &  &  &  &  &  & &  &  & n & n \\
-
-            String \textbf{to-int} &  &  &  &  &  & &  &  & n & n \\
-
-            String \textbf{to-lowercase} &  &  &  &  &  & &  &  & n & n \\
-
-            String \textbf{to-uppercase} &  &  &  &  &  & &  &  & n & n \\
-
-            String \textbf{trim-left} &  &  &  &  &  &  &  &  & n & n \\
-
-            String \textbf{trim-righ} &  &  &  &  &  & &  &  & n & n \\
-
-            String \textbf{reverse} &  &  &  &  &  & &  &  & n & 1 \\
-
-            \textbf{remove} substring by positions &  &  &  &  &  & &  &  &  & \\
-
-            String \textbf{uncapitalize} &  &  &  &  &  & &  &  &  & \\
-
-            Get string \textbf{as-bytes} &  &  &  &  &  & &  &  &  & \\
-
-            String \textbf{pop-back} &  &  &  &  &  & &  &  &  & \\
-
-            Get string \textbf{as-chars} &  &  &  &  &  & &  &  &  & \\
-
-            Get string \textbf{as-canonical} &  &  &  &  &  & &  &  &  & \\
-
-            Check if \textbf{is-ascii}  &  &  &  &  &  & &  &  &  & \\
-
-            String \textbf{copy} &  &  &  &  &  & &  &  &  & \\
-
-            String \textbf{contains-any} &  &  &  &  &  & &  &  &  & \\
-
-            String \textbf{reserve-capacity} &  &  &  &  &  & &  &  &  & \\
-
-            String \textbf{shrink-to-fit} &  &  &  &  &  & &  &  &  & \\ \hline
-
+            String \textbf{capitalize} & & $\checkmark$ & & $\checkmark$ & & $\checkmark$ & & $\checkmark$ & $\checkmark$ & \\
+            Get \textbf{char-at} a given position & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & & $\checkmark$ & & $\checkmark$ \\
+            Strings \textbf{compare} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & \\
+            Strings \textbf{compare-ignore-case} & $\checkmark$ & & $\checkmark$ & $\checkmark$ & & & & $\checkmark$ & $\checkmark$ & \\
+            Strings \textbf{concatenate} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+            Check if \textbf{contains} substring & $\checkmark$ & $\checkmark$ & & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+            \textbf{count} of substring in string & & $\checkmark$ & & $\checkmark$ & & $\checkmark$ & & & $\checkmark$ & \\
+            Check if \textbf{ends-with} a substring & $\checkmark$ & $\checkmark$ & & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+            Check if \textbf{equals} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+            \textbf{find-first} substring in string & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+            \textbf{find-last} substring in string & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+            \textbf{format} string by regexp & $\checkmark$ & $\checkmark$ & & $\checkmark$ & & & $\checkmark$ & $\checkmark$ & & \\
+            Get string \textbf{hash} & $\checkmark$ & $\checkmark$ & & $\checkmark$ & & $\checkmark$ & $\checkmark$ & $\checkmark$ & & $\checkmark$ \\
+            \textbf{insert} in string by index & $\checkmark$ & & $\checkmark$ & $\checkmark$ & & & $\checkmark$ & $\checkmark$ & & $\checkmark$ \\
+            Check if \textbf{is-alphabetic} & $\checkmark$ & $\checkmark$ & $\checkmark$ & & & & & & & \\
+            Check if \textbf{is-empty} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & & & & $\checkmark$ & & $\checkmark$ \\
+            Check if \textbf{is-whitespace} & & $\checkmark$ & $\checkmark$ & & & & $\checkmark$ & & & \\
+            \textbf{join} list of strings & & $\checkmark$ & & & & $\checkmark$ & $\checkmark$ & & $\checkmark$ & \\
+            Get string \textbf{length} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+            Check if string \textbf{matches-regexp} & $\checkmark$ & $\checkmark$ & & $\checkmark$ & $\checkmark$ & & & & & \\
+            Get string \textbf{partition} & & $\checkmark$ & & $\checkmark$ & & $\checkmark$ & & & & \\
+            \textbf{repeat} string number of times & & & & & $\checkmark$ & $\checkmark$ & & & $\checkmark$ & $\checkmark$ \\
+            \textbf{replace-all} substrings by other & $\checkmark$ & $\checkmark$ & & & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+            \textbf{replace-first} substrings by other & $\checkmark$ & $\checkmark$ & & & & $\checkmark$ & & & & $\checkmark$ \\
+            String \textbf{split} & $\checkmark$ & $\checkmark$ & & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+            Check if \textbf{starts-with} a substring & $\checkmark$ & $\checkmark$ & & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+            String \textbf{strip} & $\checkmark$ & $\checkmark$ & & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+            Get \textbf{substring} by positions & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+            String \textbf{to-float} & & & $\checkmark$ & $\checkmark$ & & & & $\checkmark$ & & \\
+            String \textbf{to-int} & & & $\checkmark$ & $\checkmark$ & & & & $\checkmark$ & & \\
+            String \textbf{to-lowercase} & $\checkmark$ & $\checkmark$ & & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+            String \textbf{to-uppercase} & $\checkmark$ & $\checkmark$ & & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+            String \textbf{trim-left} & & $\checkmark$ & & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & & $\checkmark$ & $\checkmark$ \\
+            String \textbf{trim-right} & & $\checkmark$ & & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & & $\checkmark$ & $\checkmark$ \\
+            \textbf{remove} substring by positions & & & $\checkmark$ & $\checkmark$ & & & $\checkmark$ & $\checkmark$ & & $\checkmark$ \\
+            Get string \textbf{as-bytes} & & $\checkmark$ & & $\checkmark$ & & & & & & $\checkmark$ \\
+            String \textbf{pop-back} & & & $\checkmark$ & $\checkmark$ & & & & $\checkmark$ & & $\checkmark$ \\
+            Get string \textbf{as-chars} & $\checkmark$ & & & $\checkmark$ & & & $\checkmark$ & & & $\checkmark$ \\
+            Get string \textbf{as-canonical} & $\checkmark$ & & $\checkmark$ & $\checkmark$ & & & $\checkmark$ & & & \\
+            Check if \textbf{is-ascii} & & $\checkmark$ & & $\checkmark$ & & & & & & $\checkmark$ \\
+            String \textbf{copy} & $\checkmark$ & & $\checkmark$ & & & $\checkmark$ & $\checkmark$ & & & \\
+            String \textbf{reserve-capacity} & & & $\checkmark$ & & & & & $\checkmark$ & & $\checkmark$ \\
+            String \textbf{reverse} & & $\checkmark$ & & $\checkmark$ & $\checkmark$ & & & $\checkmark$ & $\checkmark$ & \\
+            \\ \hline
         \end{tabular}
